### 2024-02-11 outputs/paper/paper.qmd
change

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
install.packages("haven")  # Install the haven package
library(haven)  # Load the haven package
library(tidyverse)
library(palmerpenguins)
library(dplyr)
```

# Introduction

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}
@fig-country
```{r fig.height=8, fig.width=10 }
#| label: fig-country
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

data <-  read.csv(file = here::here("outputs/data/clean_country_data.csv"))

data <- data[order(-data$prison_population_rate), ]

# Create the bar plot
plot <- ggplot(data, aes(x =prison_population_rate, y = country)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5)) +  # Rotate x-axis labels
  labs(x = "Prison Population Rate", y = "country") +  # Add axis labels
  ggtitle("Prison Population Rate by Country ")  # Add title

print(plot)

```

Some of our data is of penguins (@fig-bill), from @palmerpenguins.
```{r fig.height=8, fig.width=10 }
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

# Reading data
# Read CSV file using here::here() for file path and header = TRUE
x <- read.csv(file = here::here("inputs/data/all-states-history.csv"), header = TRUE)

x1218 <- x[x$date == "2020-12-18",]   # Subset data for 12/18/2020

# Ensure 'pop' column name is provided correctly in read_csv
pop <- read.csv(file = here::here("inputs/data/statepop.csv"), header = FALSE)

# Ensure 'pop' is extracted correctly from 'pop' data frame
ind <- match(x1218$state, pop[,2])

# Assign state population to x1218$pop
x1218$pop <- pop[ind,3]

# Calculate case rate for x1218
x1218$ccr <- x1218$positive / (x1218$pop * 1e6)
x1 <- read.csv(file = here::here("inputs/data/COVID-19 Cases in State and Federal Prison Systems.csv"),
               header=T)

x1 <- lapply(x1, function(i) { sub(",", "", i) })                    # data cleaning
x1 <- lapply(x1, function(i) { sub("NR", NA, i) })
x1[names(x1)[c(2:7,9)]]  <- lapply(x1[names(x1)[c(2:7,9)]], as.numeric)
x1$incpop <- x1$Incarcerated.Positive/x1$Incarcerated.Case.rate.per.1.000

ind <- match(x1218$state, x1$Prison.System)                           # matching states
ccr <- data.frame(pop=1000*x1218$ccr,
                  prisn=x1$Incarcerated.Case.rate.per.1.000[ind],
                  state=x1$state[ind])                               # case rate dataframe
ccr <- ccr[complete.cases(ccr),]

o1 <- order(ccr[,2])
n1 <- length(o1)

par(fig=c(.1,1,0,1))
plot(ccr[o1,2], 1:n1, pch="", xlim=c(0,800), xlab="", ylab="", yaxt='n')
abline(h=1:n1, lty=5, col="gray")
axis(1)
points(ccr[o1,1], 1:n1, pch=17, col="blue")
points(ccr[o1,2], 1:n1, pch=16, col="red")
mtext(ccr$state[o1], side=2, at=1:n1, las=1, line=.5, cex=.75)
legend(450, 7, c("Prison","General population"), pch=c(16, 17),
       col=c("red","blue"), bty="n", cex=1.1)

```

```{r fig.height=8, fig.width=10}
#| label: fig-bills2
#| fig-cap: Bills of penguins
#| echo: false

x <- read.csv(file = here::here("inputs/data/all-states-history.csv"), header = TRUE)

x1218 <- x[x$date == "2020-12-18",]   # Subset data for 12/18/2020

# Ensure 'pop' column name is provided correctly in read_csv
pop <- read.csv(file = here::here("inputs/data/statepop.csv"), header = FALSE)

# Ensure 'pop' is extracted correctly from 'pop' data frame
ind <- match(x1218$state, pop[,2])

# Assign state population to x1218$pop
x1218$pop <- pop[ind,3]

# Calculate case rate for x1218
x1218$ccr <- x1218$positive / (x1218$pop * 1e6)
x2 <- read.csv(file = here::here("inputs/data/COVID-19 Cases in State and Federal Prison Systems.csv"), header = TRUE)

# Data cleaning
x2 <- lapply(x2, function(i) { gsub(",", "", i) })  # Remove commas
x2 <- lapply(x2, function(i) { gsub("NR", NA, i) })  # Replace "NR" with NA
x2[names(x2)[c(2:7, 9)]] <- lapply(x2[names(x2)[c(2:7, 9)]], as.numeric)  # Convert selected columns to numeric
x2$incpop <- x2$Staff.Positive / x2$Staff.Case.rate.per.1.000

# Match states
ind <- match(x1218$state, x2$Prison.System)

# Create case rate dataframe
ccr <- data.frame(pop = 1000 * x1218$ccr,
                  prisn = x2$Staff.Case.rate.per.1.000[ind],
                  state = x2$state[ind])

# Remove rows with NAs
ccr <- ccr[complete.cases(ccr),]

# Plotting
o1 <- order(ccr[, 2])
n1 <- length(o1)

par(fig=c(.1,1,0,1))

plot(ccr[o1, 2], 1:n1, pch="", xlim=c(0, 800), xlab="", ylab="", yaxt='n')
abline(h=1:n1, lty=5, col="gray")
axis(1)
points(ccr[o1, 1], 1:n1, pch=17, col="blue")
points(ccr[o1, 2], 1:n1, pch=16, col="green")
mtext(ccr$state[o1], side=2, at=1:n1, las=1, line=.5, cex=.75)
legend(450, 7, c("Staff", "General population"), pch=c(16, 17),
       col=c("green", "blue"), bty="n", cex=1.1)

```

```{r }
#| label: fig-plane
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

data_1 <- read_dta('../../inputs/data/spi86to16.dta')

x <- data_1[data_1$admit==0,]

drugev  <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(drugev, wt, na.rm=T)))
drugev  <- drugev[!is.nan(drugev[,3]),]
vocev   <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(vocev, wt, na.rm=T)))
vocev   <- data.matrix(vocev[!is.nan(vocev[,3]),])
work    <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(work, wt, na.rm=T)))
work    <- data.matrix(work[!is.nan(work[,3]),])
edev    <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(edev, wt, na.rm=T)))
edev    <- data.matrix(edev[!is.nan(edev[,3]),])

dimnames(drugev) <- dimnames(vocev) <- dimnames(work) <- dimnames(edev) <-
  list(NULL, c("region","year","xbar"))

par(mfrow=c(1,4))
par(fig=c(0,.29, 0,1))
plot(drugev[drugev[,"region"]==1,"year"],
     drugev[drugev[,"region"]==1,"xbar"]*100,
     type="b", pch=16, main="Drug Program",
     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
     axes=F, ylab="Percent", xlab="")
axis(1)
axis(2)
lines(drugev[drugev[,"region"]==2,"year"], drugev[drugev[,"region"]==2,"xbar"]*100,
      type="b", pch=17, col="dodgerblue")
lines(drugev[drugev[,"region"]==3,"year"], drugev[drugev[,"region"]==3,"xbar"]*100,
      type="b", pch=18, col="red")
lines(drugev[drugev[,"region"]==4,"year"], drugev[drugev[,"region"]==4,"xbar"]*100,
      type="b", pch=19, col="blue")
legend(1986, 80, c("Northeast","Midwest","South","West"),
       pch=16:19, col=c("skyblue2", "dodgerblue", "red","blue"),
       lty=1, bty="n", cex=1.1)
abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
par(new=T)
par(fig=c(.237,.527, 0,1))
plot(edev[edev[,"region"]==1,"year"],
     edev[edev[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Education",
     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
     axes=F, ylab="", xlab="")
axis(1)
lines(edev[edev[,"region"]==2,"year"], edev[edev[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
lines(edev[edev[,"region"]==3,"year"], edev[edev[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
lines(edev[edev[,"region"]==4,"year"], edev[edev[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
par(new=T)
par(fig=c(.473,.763, 0,1))
plot(vocev[vocev[,"region"]==1,"year"],
     vocev[vocev[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Job Training",
     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
     axes=F, ylab="", xlab="")
axis(1)
lines(vocev[vocev[,"region"]==2,"year"], vocev[vocev[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
lines(vocev[vocev[,"region"]==3,"year"], vocev[vocev[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
lines(vocev[vocev[,"region"]==4,"year"], vocev[vocev[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
par(new=T)
par(fig=c(.71,1.0, 0,1))
plot(work[work[,"region"]==1,"year"],
     work[work[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Work",
     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
     axes=F, ylab="", xlab="")
axis(1)
lines(work[work[,"region"]==2,"year"], work[work[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
lines(work[work[,"region"]==3,"year"], work[work[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
lines(work[work[,"region"]==4,"year"], work[work[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)

```

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

\newpage

# References

### 2024-02-11 paper/paper.qmd
change

--- 2024-02-11 outputs/paper/paper.qmd
@@
 #| message: false
-install.packages("haven")  # Install the haven package
-library(haven)  # Load the haven package
+
 library(tidyverse)
 library(palmerpenguins)
-library(dplyr)
+library(readr)
 ```
@@
 
-The remainder of this paper is structured as follows. @sec-data....
+The remainder of this paper is structured as follows.
 
-# Data {#sec-data}
-@fig-country
-```{r fig.height=8, fig.width=10 }
-#| label: fig-country
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
+# Data 
+## Source
 
-data <-  read.csv(file = here::here("outputs/data/clean_country_data.csv"))
+## Methodology
+All data are not obtained directly through surveys/interviews, but are processed and calculated based on existing data.
 
-data <- data[order(-data$prison_population_rate), ]
+ mass incarceration.xlsx
 
-# Create the bar plot
-plot <- ggplot(data, aes(x =prison_population_rate, y = country)) +
-  geom_bar(stat = "identity", fill = "skyblue") +
-  theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5)) +  # Rotate x-axis labels
-  labs(x = "Prison Population Rate", y = "country") +  # Add axis labels
-  ggtitle("Prison Population Rate by Country ")  # Add title
+ incarceration 1925-2019
 
-print(plot)
+## Features
+mass incarceration.xlsx
 
-```
+ incarceration 1925-2019
+ year :1925-2019
+ Prison :integer number
+ Prison rate per(100k) easy to read and compare
+ Jail
+ Total
+ Population
+ Total Rate
 
-Some of our data is of penguins (@fig-bill), from @palmerpenguins.
+ world incarceration rates
+ rate
+ rate18
+
+ cumulative risk
+ race :w(white) b(black)
+ education
+ cohort
+ risk
+
+Talk more about it.
+
+And also planes (@fig-planes).
+(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+
 ```{r fig.height=8, fig.width=10 }
@@
 ```
+
+Talk way more about it. 
+(@fig-bills2)
 
@@
 
-```{r }
-#| label: fig-plane
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-data_1 <- read_dta('../../inputs/data/spi86to16.dta')
-
-x <- data_1[data_1$admit==0,]
-
-drugev  <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(drugev, wt, na.rm=T)))
-drugev  <- drugev[!is.nan(drugev[,3]),]
-vocev   <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(vocev, wt, na.rm=T)))
-vocev   <- data.matrix(vocev[!is.nan(vocev[,3]),])
-work    <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(work, wt, na.rm=T)))
-work    <- data.matrix(work[!is.nan(work[,3]),])
-edev    <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(edev, wt, na.rm=T)))
-edev    <- data.matrix(edev[!is.nan(edev[,3]),])
-
-dimnames(drugev) <- dimnames(vocev) <- dimnames(work) <- dimnames(edev) <-
-  list(NULL, c("region","year","xbar"))
-
-par(mfrow=c(1,4))
-par(fig=c(0,.29, 0,1))
-plot(drugev[drugev[,"region"]==1,"year"],
-     drugev[drugev[,"region"]==1,"xbar"]*100,
-     type="b", pch=16, main="Drug Program",
-     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
-     axes=F, ylab="Percent", xlab="")
-axis(1)
-axis(2)
-lines(drugev[drugev[,"region"]==2,"year"], drugev[drugev[,"region"]==2,"xbar"]*100,
-      type="b", pch=17, col="dodgerblue")
-lines(drugev[drugev[,"region"]==3,"year"], drugev[drugev[,"region"]==3,"xbar"]*100,
-      type="b", pch=18, col="red")
-lines(drugev[drugev[,"region"]==4,"year"], drugev[drugev[,"region"]==4,"xbar"]*100,
-      type="b", pch=19, col="blue")
-legend(1986, 80, c("Northeast","Midwest","South","West"),
-       pch=16:19, col=c("skyblue2", "dodgerblue", "red","blue"),
-       lty=1, bty="n", cex=1.1)
-abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
-par(new=T)
-par(fig=c(.237,.527, 0,1))
-plot(edev[edev[,"region"]==1,"year"],
-     edev[edev[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Education",
-     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
-     axes=F, ylab="", xlab="")
-axis(1)
-lines(edev[edev[,"region"]==2,"year"], edev[edev[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
-lines(edev[edev[,"region"]==3,"year"], edev[edev[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
-lines(edev[edev[,"region"]==4,"year"], edev[edev[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
-abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
-par(new=T)
-par(fig=c(.473,.763, 0,1))
-plot(vocev[vocev[,"region"]==1,"year"],
-     vocev[vocev[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Job Training",
-     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
-     axes=F, ylab="", xlab="")
-axis(1)
-lines(vocev[vocev[,"region"]==2,"year"], vocev[vocev[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
-lines(vocev[vocev[,"region"]==3,"year"], vocev[vocev[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
-lines(vocev[vocev[,"region"]==4,"year"], vocev[vocev[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
-abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
-par(new=T)
-par(fig=c(.71,1.0, 0,1))
-plot(work[work[,"region"]==1,"year"],
-     work[work[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Work",
-     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
-     axes=F, ylab="", xlab="")
-axis(1)
-lines(work[work[,"region"]==2,"year"], work[work[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
-lines(work[work[,"region"]==3,"year"], work[work[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
-lines(work[work[,"region"]==4,"year"], work[work[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
-abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
-
-```
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-Talk way more about it.
-
-# Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
 # Results
 
-Our results are summarized in @tbl-modelresults.
+Our results are summarized in
 
@@
 
-## First discussion point {#sec-first-point}
+## First discussion point
 
@@
 
-# Model details {#sec-model-details}
+# Model details
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
 ## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
 

### 2024-02-11 scripts/01-download_data.R

@@ -16,11 +16,23 @@ library(tidyverse)
 #### Download data ####
 # [...ADD CODE HERE TO DOWNLOAD...]
 
+# Load required library
+library(rvest)
+
+# Define the URL of the webpage
+url <- "https://www.prisonstudies.org/highest-to-lowest/prison_population_rate?field_region_taxonomy_tid=All"
+
+# Read the webpage
+page <- read_html(url)
+
+# Extract the table containing the data
+table_data <- html_table(page)[[1]]  # Assuming the data is in the first table
+
+# Save the data to a CSV file
 
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+
+write_csv(table_data, "inputs/data/country_data.csv") 
 
          

### 2024-02-11 scripts/02-data_cleaning.R

@@ -11,34 +11,19 @@
 library(tidyverse)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+raw_data <- read_csv("inputs/data/country_data.csv")
 
 cleaned_data <-
   raw_data |>
   janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+  select(title, prison_population_rate) |>
+  filter(title%in% c ("United States of America","Turkey","United Kingdom: England & Wales","Spain",
+                         "France","Austria", "Italy","Belgium","Switzerland",
+                      "Ireland", "Germany" ,"Denmark" ,"Norway","Netherlands", "Sweden",
+                      "Finland","Chile","Canada","Norway","Singapore","Japan","Brazil"))|>
+rename(country=title)
+
+ 
 
 #### Save data ####
-write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+write_csv(cleaned_data, "outputs/data/clean_country_data.csv")

### 2024-02-11 outputs/paper/paper.qmd
update

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Delving into the World Inside Prisons for Safety, Health, and Isolation"
+
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: LINK."
+  - Dong Jun Yoon
+  - Sirui Tan
+thanks: "Code and data are available at: https://github.com/siru1366/us-mass-incarceration.git."
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This social science research focuses on the impact of prisons on crime rates and socioeconomic disparities.
+However, the penal institutions are often disregarded, creating a significant gap in understanding its true effect.
+This paper takes a look at the prison, their function in rehabilitation efforts, their role as setting for violence, healthcare provision, and the isolation experienced in solitary confinement.
+Recent studies indicate that fewer inmates are involved in programs now compared to the 1980’s, and prisoners face more violence, sickness, and isolation.
+These conditions question if prisons are really treating people with dignity and respect, and how these acts will affect people who recently joined the society again.
+"
 format: pdf
@@
 install.packages("haven")  # Install the haven package
+install.packages("openxlsx")
+library(openxlsx)
 library(haven)  # Load the haven package
@@
 
-You can and should cross-reference sections and sub-sections.
+This paper explores how prisons impact crime and inequality.
+Prisons are often overlooked compared to other institutions such as schools or hospitals.
+We are focusing on the US, where the concept of “mass incarceration” is a big issue, in other words there are a lot of people in prison, especially Black men with limited education.
+This mostly happens due to strict laws against Black men and inequality that rise upon the issue.
+Researchers have studied incarceration in various angles, examining its effects on how prisons affect crime rates, labor markets, health outcomes, and family dynamics.
+Despite debates over rehabilitation, it is still hard for them to get jobs and be accepted in society.
+This paper takes a unique perspective, where we view US penal institutions as “total institutions” where individuals face constricted control and minimal autonomy.
+We are exploring key issues such as overcrowding, violence, health challenges, and the harsh realities of solitary confinement.
+By understanding what happens inside prisons, we can gain a deeper understanding of the problems of mass incarceration and work towards making things better.
+→ We can add details after we decide what data and model we are going to use (Ex. Rate has increased 80% over 1990 to 2020)
 
@@
 # Data {#sec-data}
+
+##Source
+The paper used for replication is "Inside the Box: Safety, Health, and Isolation in Prison," which mainly analyzes the impact of prisons on safety and health, and specifically includes data from the new coronavirus pandemic.
+
+Sourcebook of Criminal Justice Statistics, Bureau of Justice Statistics Report, Jail Inmates in 2018, U.S. Population FRED Data, World Prison Population Data, and Western B. and Pettit B data
+
+## Methodology
+All data are not obtained directly through surveys or sampling statistics; rather, they are derived through meticulous processing and calculation based on pre-existing datasets.
+
+ mass incarceration.xlsx
+
+ incarceration 1925-2019
+
+## Features
+mass incarceration.xlsx
+
+ incarceration 1925-2019
+ Year:1925-2019
+ Prison: integer number
+ Prison rate per(100k) : easy to read and compare
+ Jail
+ Total
+ Population
+ Total Rate
+
+ world incarceration rates
+ rate
+ rate18
+
+ cumulative risk
+ race :w(white) b(black) Lack of data on other ethnic minorities
+
+ education
+ cohort
+ risk
+
+COVID-19 Cases in State and Federal Prison Systems.csv：
+Prison System
+Incarcerated Tested
+Incarcerated Positive,
+Incarcerated Deaths,
+Staff Positive,
+Staff Deaths,
+Incarcerated Case rate per 1,000
+Scrape Date
+Staff Case rate per 1,000
+state
+
+statepop.csv:
+sate
+abbreviation
+
+all-states-history.csv:
+
+## Measurement:
+Enrollment in Drug, Education, Job Training Programs, and Work Assignment, State Prisoners, by Region
+Original data comes from two prison questionnaires
+For example, the sample for the 2004 survey was drawn from two different documents.
+The primary archive includes a list of 1,549 state prisons from the June 30, 2000, BJS 2000 Census of State and Federal Correctional Facilities.
+The secondary archive includes 36 prisons open between June 30, 2000, and April 1, 2003.
+The sampling design required a stratified two-stage selection process.
+In the initial phase, 14 male and 7 female facilities were identified based on the gender ratio within prisons.
+The remaining facilities are divided into 16 levels based on geographic region and the male and female population within each prison.
+The weighting procedure involves assigning each inmate a base weight and three adjustment factors to obtain the final weight for the survey.
+Data was collected through face-to-face interviews with prisoners using computer-assisted personal interviewing techniques.
+
+Cumulative COVID-19 Case Rates among Those in Prison and General Population, by State: March 2020 to January 2021
+
+# Result
+## Over trend
+@fig-over
+```{r fig.height=10, fig.width=6 }
+#| label: fig-over
+#| fig-cap: US Incarceration, 1925-2018
+#| echo: false
+#| warning: false
+#| message: false
+
+library(openxlsx)
+
+file_path <- here::here("inputs/data/mass incarceration.xlsx")
+
+# Read the Excel file
+x0 <- read.xlsx(file_path, sheet = 1)
+par(mfrow=c(3,1))
+par(fig=c(.05,.95, 2/3-.02, 1))
+plot(x0$Year, x0$Prison.Rate.per.100k, type="l", col="blue",
+     xlim=c(1920, 2020), ylim=c(0, 800),
+     xlab="", ylab="Incarceration Rate (per 100,000)", lty=1, lwd=2)
+title(" US Incarceration, 1925-2018")
+lines(x0$Year, x0$TotalRate, lty=2, col="red", lwd=2)
+legend(1925, 770, c("Prison and jail","Prison only"), lwd=2,
+       lty=c(2,1), col=c("red","blue"), bty="n")
+abline(h=seq(0, 800, 200), v=seq(1920,2020,20), lty=3, col="gray")
+
+```
+
 @fig-country

### 2024-02-11 outputs/paper/paper.qmd
updat

@@
 
-##Source
+## Source
 The paper used for replication is "Inside the Box: Safety, Health, and Isolation in Prison," which mainly analyzes the impact of prisons on safety and health, and specifically includes data from the new coronavirus pandemic.
@@
 ## Over trend
+
+Mass incarceration, as outlined by Garland (2001), refers to the historical phenomenon characterized by exceptionally high rates of imprisonment, particularly affecting marginalized populations.
+It signifies the confinement of vast numbers of individuals within prisons, coupled with the enduring legal and financial barriers they encounter upon reintegration into society, as described by Younes (2014).
+
+From 1925 to 1972, the incarceration rate in the United States exhibited a period of relative stability, punctuated by minor fluctuations.
+However, since the 1970s, the number of inmates in the U.S.
+has surged dramatically, increasing by over sixfold, as noted by Manza and Uggen (2006: 95).
+Following its peak in 2007, incarceration rates have seen a slight decline over the past decade.
+However, they remain approximately five times higher than the average rate observed throughout the 20th century.
+
+This underscores the continued importance of mass incarceration as a pressing issue in the United States.
+It highlights the need for further research to fully examine its effects on various aspects including health, property ownership and personal growth.
+Furthermore, understanding its socioeconomic impact and exploring effective rehabilitation and reintegration strategies are important steps to address this multifaceted problem and build a more just and equitable society.
 @fig-over
@@
 ```
+In addition to examining the trajectory of incarceration rates within the United States over time, it is equally imperative to conduct horizontal comparisons by scrutinizing incarceration rates across different countries.
+Such comparisons enable us to discern whether mass incarceration is a global phenomenon or if it manifests as a more acute issue within the United States.
+\ Data regarding prison population rates per 100,000 of the national population is accessible through the online public data platform World Prison Brief.
+This resource provides updated country information on a monthly basis, drawing primarily from governmental or other authoritative sources, thereby ensuring the data's timeliness and reliability.
+\ After acquiring the most recent data, we encountered complexity in processing the information for over 200 countries.
+Consequently, we streamlined our analysis by selecting a subset of 20 representative countries.
+Subsequently, we utilized this refined dataset to generate informative charts and visualizations.
+
+\ It can be readily inferred from graphical representations and pertinent research that the United States holds the title of the world's foremost incarcerator, detaining a higher percentage of its population than any other nation.
 
@@
 ```
+```{r fig.height=6, fig.width=8}
+#| label: fig-admit
+#| fig-cap: Relationship between wing length and width
+#| echo: false
+#| warning: false
+#| message: false
 
-```{r }
+data_1 <- read_dta('../../inputs/data/spi86to16.dta')
+
+x <- data_1[data_1$admit==1,]
+
+drugev  <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(drugev, wt, na.rm=T)))
+drugev  <- drugev[!is.nan(drugev[,3]),]
+vocev   <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(vocev, wt, na.rm=T)))
+vocev   <- data.matrix(vocev[!is.nan(vocev[,3]),])
+work    <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(work, wt, na.rm=T)))
+work    <- data.matrix(work[!is.nan(work[,3]),])
+edev    <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(edev, wt, na.rm=T)))
+edev    <- data.matrix(edev[!is.nan(edev[,3]),])
+
+dimnames(drugev) <- dimnames(vocev) <- dimnames(work) <- dimnames(edev) <-
+  list(NULL, c("region","year","xbar"))
+
+par(mfrow=c(1,4))
+par(fig=c(0,.29, 0,1))
+plot(drugev[drugev[,"region"]==1,"year"],
+     drugev[drugev[,"region"]==1,"xbar"]*100,
+     type="b", pch=16, main="Drug Program",
+     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
+     axes=F, ylab="Percent", xlab="")
+axis(1)
+axis(2)
+lines(drugev[drugev[,"region"]==2,"year"], drugev[drugev[,"region"]==2,"xbar"]*100,
+      type="b", pch=17, col="dodgerblue")
+lines(drugev[drugev[,"region"]==3,"year"], drugev[drugev[,"region"]==3,"xbar"]*100,
+      type="b", pch=18, col="red")
+lines(drugev[drugev[,"region"]==4,"year"], drugev[drugev[,"region"]==4,"xbar"]*100,
+      type="b", pch=19, col="blue")
+legend(1986, 80, c("Northeast","Midwest","South","West"),
+       pch=16:19, col=c("skyblue2", "dodgerblue", "red","blue"),
+       lty=1, bty="n", cex=1.1)
+abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
+par(new=T)
+par(fig=c(.237,.527, 0,1))
+plot(edev[edev[,"region"]==1,"year"],
+     edev[edev[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Education",
+     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
+     axes=F, ylab="", xlab="")
+axis(1)
+lines(edev[edev[,"region"]==2,"year"], edev[edev[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
+lines(edev[edev[,"region"]==3,"year"], edev[edev[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
+lines(edev[edev[,"region"]==4,"year"], edev[edev[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
+abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
+par(new=T)
+par(fig=c(.473,.763, 0,1))
+plot(vocev[vocev[,"region"]==1,"year"],
+     vocev[vocev[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Job Training",
+     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
+     axes=F, ylab="", xlab="")
+axis(1)
+lines(vocev[vocev[,"region"]==2,"year"], vocev[vocev[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
+lines(vocev[vocev[,"region"]==3,"year"], vocev[vocev[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
+lines(vocev[vocev[,"region"]==4,"year"], vocev[vocev[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
+abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
+par(new=T)
+par(fig=c(.71,1.0, 0,1))
+plot(work[work[,"region"]==1,"year"],
+     work[work[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Work",
+     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
+     axes=F, ylab="", xlab="")
+axis(1)
+lines(work[work[,"region"]==2,"year"], work[work[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
+lines(work[work[,"region"]==3,"year"], work[work[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
+lines(work[work[,"region"]==4,"year"], work[work[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
+abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
+
+```
+
+@fig-plane
+
+```{r fig.height=6, fig.width=8 }
 #| label: fig-plane
@@
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
 Talk way more about it.
 
-# Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
 We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
-
-Our results are summarized in @tbl-modelresults.
 

### 2024-02-11 scripts/02-data_cleaning.R

@@ -17,10 +17,10 @@ cleaned_data <-
   raw_data |>
   janitor::clean_names() |>
   select(title, prison_population_rate) |>
-  filter(title%in% c ("United States of America","Turkey","United Kingdom: England & Wales","Spain",
+  filter(title%in% c ("United States of America","Croatia","United Kingdom: England & Wales","Spain",
                          "France","Austria", "Italy","Belgium","Switzerland",
                       "Ireland", "Germany" ,"Denmark" ,"Norway","Netherlands", "Sweden",
-                      "Finland","Chile","Canada","Norway","Singapore","Japan","Brazil"))|>
+                      "Finland","Egypt","Canada","Norway","Singapore","Japan","Iceland"))|>
 rename(country=title)
 
  

### 2024-02-11 outputs/paper/paper.qmd
update

@@
 thanks: "Code and data are available at: https://github.com/siru1366/us-mass-incarceration.git."
-date: today
+date:  February 09, 2024
 date-format: long
@@
 ```
+## Comparing
 In addition to examining the trajectory of incarceration rates within the United States over time, it is equally imperative to conduct horizontal comparisons by scrutinizing incarceration rates across different countries.
 Such comparisons enable us to discern whether mass incarceration is a global phenomenon or if it manifests as a more acute issue within the United States.
+
 \ Data regarding prison population rates per 100,000 of the national population is accessible through the online public data platform World Prison Brief.
 This resource provides updated country information on a monthly basis, drawing primarily from governmental or other authoritative sources, thereby ensuring the data's timeliness and reliability.
+
 \ After acquiring the most recent data, we encountered complexity in processing the information for over 200 countries.
 Consequently, we streamlined our analysis by selecting a subset of 20 representative countries.
-Subsequently, we utilized this refined dataset to generate informative charts and visualizations.
+Subsequently, we utilized this refined dataset to generate informative charts and visualizations(@fig-country)
+
+\ In addition to the United States, which serves as the primary focus of our research, the selected subset of 19 countries encompasses a diverse range of geographical locations across all seven continents.
+These countries represent various levels of development, including developed nations, developing regions, and areas classified as less economically developed.
+Moreover, the chosen countries vary in terms of land area, with some comparable in size to the United States, such as Canada and, to a lesser extent, Iceland.
+This diverse selection ensures a comprehensive analysis that accounts for a wide spectrum of geographic, developmental, and size-related factors.
 
@@
 
-@fig-country
+\ It is noteworthy that the incarceration rates (per 100,000) observed in the other 19 countries typically hover around 100.
+In stark contrast, the United States exhibits an incarceration rate exceeding four times this average.
+This significant disparity underscores the exceptional nature of the U.S.
+incarceration system compared to its international counterparts.
+
 ```{r fig.height=8, fig.width=10 }
@@
 
-Some of our data is of penguins (@fig-bill), from @palmerpenguins.
-```{r fig.height=8, fig.width=10 }
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-# Reading data
-# Read CSV file using here::here() for file path and header = TRUE
-x <- read.csv(file = here::here("inputs/data/all-states-history.csv"), header = TRUE)
-
-x1218 <- x[x$date == "2020-12-18",]   # Subset data for 12/18/2020
-
-# Ensure 'pop' column name is provided correctly in read_csv
-pop <- read.csv(file = here::here("inputs/data/statepop.csv"), header = FALSE)
-
-# Ensure 'pop' is extracted correctly from 'pop' data frame
-ind <- match(x1218$state, pop[,2])
-
-# Assign state population to x1218$pop
-x1218$pop <- pop[ind,3]
-
-# Calculate case rate for x1218
-x1218$ccr <- x1218$positive / (x1218$pop * 1e6)
-x1 <- read.csv(file = here::here("inputs/data/COVID-19 Cases in State and Federal Prison Systems.csv"),
-               header=T)
-
-x1 <- lapply(x1, function(i) { sub(",", "", i) })                    # data cleaning
-x1 <- lapply(x1, function(i) { sub("NR", NA, i) })
-x1[names(x1)[c(2:7,9)]]  <- lapply(x1[names(x1)[c(2:7,9)]], as.numeric)
-x1$incpop <- x1$Incarcerated.Positive/x1$Incarcerated.Case.rate.per.1.000
-
-ind <- match(x1218$state, x1$Prison.System)                           # matching states
-ccr <- data.frame(pop=1000*x1218$ccr,
-                  prisn=x1$Incarcerated.Case.rate.per.1.000[ind],
-                  state=x1$state[ind])                               # case rate dataframe
-ccr <- ccr[complete.cases(ccr),]
-
-o1 <- order(ccr[,2])
-n1 <- length(o1)
-
-par(fig=c(.1,1,0,1))
-plot(ccr[o1,2], 1:n1, pch="", xlim=c(0,800), xlab="", ylab="", yaxt='n')
-abline(h=1:n1, lty=5, col="gray")
-axis(1)
-points(ccr[o1,1], 1:n1, pch=17, col="blue")
-points(ccr[o1,2], 1:n1, pch=16, col="red")
-mtext(ccr$state[o1], side=2, at=1:n1, las=1, line=.5, cex=.75)
-legend(450, 7, c("Prison","General population"), pch=c(16, 17),
-       col=c("red","blue"), bty="n", cex=1.1)
-
-```
-
-```{r fig.height=8, fig.width=10}
-#| label: fig-bills2
-#| fig-cap: Bills of penguins
-#| echo: false
-
-x <- read.csv(file = here::here("inputs/data/all-states-history.csv"), header = TRUE)
-
-x1218 <- x[x$date == "2020-12-18",]   # Subset data for 12/18/2020
-
-# Ensure 'pop' column name is provided correctly in read_csv
-pop <- read.csv(file = here::here("inputs/data/statepop.csv"), header = FALSE)
-
-# Ensure 'pop' is extracted correctly from 'pop' data frame
-ind <- match(x1218$state, pop[,2])
-
-# Assign state population to x1218$pop
-x1218$pop <- pop[ind,3]
-
-# Calculate case rate for x1218
-x1218$ccr <- x1218$positive / (x1218$pop * 1e6)
-x2 <- read.csv(file = here::here("inputs/data/COVID-19 Cases in State and Federal Prison Systems.csv"), header = TRUE)
-
-# Data cleaning
-x2 <- lapply(x2, function(i) { gsub(",", "", i) })  # Remove commas
-x2 <- lapply(x2, function(i) { gsub("NR", NA, i) })  # Replace "NR" with NA
-x2[names(x2)[c(2:7, 9)]] <- lapply(x2[names(x2)[c(2:7, 9)]], as.numeric)  # Convert selected columns to numeric
-x2$incpop <- x2$Staff.Positive / x2$Staff.Case.rate.per.1.000
-
-# Match states
-ind <- match(x1218$state, x2$Prison.System)
-
-# Create case rate dataframe
-ccr <- data.frame(pop = 1000 * x1218$ccr,
-                  prisn = x2$Staff.Case.rate.per.1.000[ind],
-                  state = x2$state[ind])
-
-# Remove rows with NAs
-ccr <- ccr[complete.cases(ccr),]
-
-# Plotting
-o1 <- order(ccr[, 2])
-n1 <- length(o1)
-
-par(fig=c(.1,1,0,1))
-
-plot(ccr[o1, 2], 1:n1, pch="", xlim=c(0, 800), xlab="", ylab="", yaxt='n')
-abline(h=1:n1, lty=5, col="gray")
-axis(1)
-points(ccr[o1, 1], 1:n1, pch=17, col="blue")
-points(ccr[o1, 2], 1:n1, pch=16, col="green")
-mtext(ccr$state[o1], side=2, at=1:n1, las=1, line=.5, cex=.75)
-legend(450, 7, c("Staff", "General population"), pch=c(16, 17),
-       col=c("green", "blue"), bty="n", cex=1.1)
-
-```
 ```{r fig.height=6, fig.width=8}
@@
 ```
-
-@fig-plane
 
@@
 
-Talk way more about it.
+```{r fig.height=10, fig.width=10 }
+#| label: fig-planes
+#| fig-cap: Cumulative COVID-19 Case Rates among Those in Prison and General Population, by State
+#| echo: false
+#| warning: false
+#| message: false
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+# Reading data
+# Read CSV file using here::here() for file path and header = TRUE
+x <- read.csv(file = here::here("inputs/data/all-states-history.csv"), header = TRUE)
+
+x1218 <- x[x$date == "2020-12-18",]   # Subset data for 12/18/2020
+
+# Ensure 'pop' column name is provided correctly in read_csv
+pop <- read.csv(file = here::here("inputs/data/statepop.csv"), header = FALSE)
+
+# Ensure 'pop' is extracted correctly from 'pop' data frame
+ind <- match(x1218$state, pop[,2])
+
+# Assign state population to x1218$pop
+x1218$pop <- pop[ind,3]
+
+# Calculate case rate for x1218
+x1218$ccr <- x1218$positive / (x1218$pop * 1e6)
+x1 <- read.csv(file = here::here("inputs/data/COVID-19 Cases in State and Federal Prison Systems.csv"),
+               header=T)
+
+x1 <- lapply(x1,  function(i) { gsub(",", "", i) })                    # data cleaning
+x1 <- lapply(x1, function(i) { gsub("NR", NA, i) })
+x1[names(x1)[c(2:7,9)]]  <- lapply(x1[names(x1)[c(2:7,9)]], as.numeric)
+x1$incpop <- x1$Incarcerated.Positive/x1$Incarcerated.Case.rate.per.1.000
+
+ind <- match(x1218$state, x1$Prison.System)                           # matching states
+ccr <- data.frame(pop=1000*x1218$ccr,
+                  prisn=x1$Incarcerated.Case.rate.per.1.000[ind],
+                  state=x1$state[ind])                               # case rate dataframe
+ccr <- ccr[complete.cases(ccr),]
+
+o1 <- order(ccr[,2])
+n1 <- length(o1)
+
+par(fig=c(.1,1,0,1))
+plot(ccr[o1,2], 1:n1, pch="", xlim=c(0,800), xlab="", ylab="", yaxt='n')
+abline(h=1:n1, lty=5, col="gray")
+axis(1)
+points(ccr[o1,1], 1:n1, pch=17, col="blue")
+points(ccr[o1,2], 1:n1, pch=16, col="red")
+mtext(ccr$state[o1], side=2, at=1:n1, las=1, line=.5, cex=.75)
+legend(450, 7, c("Prison","General population"), pch=c(16, 17),
+       col=c("red","blue"), bty="n", cex=1.1)
+
+```
+
+```{r fig.height=10, fig.width=10}
+#| label: Bills of penguins
+#| fig-cap: Cumulative COVID-19 Case Rates among Those in Prison Staff and General Population
+#| echo: false
+
+x <- read.csv(file = here::here("inputs/data/all-states-history.csv"), header = TRUE)
+
+x1218 <- x[x$date == "2020-12-18",]   # Subset data for 12/18/2020
+
+# Ensure 'pop' column name is provided correctly in read_csv
+pop <- read.csv(file = here::here("inputs/data/statepop.csv"), header = FALSE)
+
+# Ensure 'pop' is extracted correctly from 'pop' data frame
+ind <- match(x1218$state, pop[,2])
+
+# Assign state population to x1218$pop
+x1218$pop <- pop[ind,3]
+
+# Calculate case rate for x1218
+x1218$ccr <- x1218$positive / (x1218$pop * 1e6)
+x2 <- read.csv(file = here::here("inputs/data/COVID-19 Cases in State and Federal Prison Systems.csv"), header = TRUE)
+
+# Data cleaning
+x2 <- lapply(x2, function(i) { gsub(",", "", i) })  # Remove commas
+x2 <- lapply(x2, function(i) { gsub("NR", NA, i) })  # Replace "NR" with NA
+x2[names(x2)[c(2:7, 9)]] <- lapply(x2[names(x2)[c(2:7, 9)]], as.numeric)  # Convert selected columns to numeric
+x2$incpop <- x2$Staff.Positive / x2$Staff.Case.rate.per.1.000
+
+# Match states
+ind <- match(x1218$state, x2$Prison.System)
+
+# Create case rate dataframe
+ccr <- data.frame(pop = 1000 * x1218$ccr,
+                  prisn = x2$Staff.Case.rate.per.1.000[ind],
+                  state = x2$state[ind])
+
+# Remove rows with NAs
+ccr <- ccr[complete.cases(ccr),]
+
+# Plotting
+o1 <- order(ccr[, 2])
+n1 <- length(o1)
+
+par(fig=c(.1,1,0,1))
+
+plot(ccr[o1, 2], 1:n1, pch="", xlim=c(0, 800), xlab="", ylab="", yaxt='n')
+abline(h=1:n1, lty=5, col="gray")
+axis(1)
+points(ccr[o1, 1], 1:n1, pch=17, col="blue")
+points(ccr[o1, 2], 1:n1, pch=16, col="green")
+mtext(ccr$state[o1], side=2, at=1:n1, las=1, line=.5, cex=.75)
+legend(450, 7, c("Staff", "General population"), pch=c(16, 17),
+       col=c("green", "blue"), bty="n", cex=1.1)
+
+```
 
@@
 
-## First discussion point {#sec-first-point}
+## Cumulative COVID-19 Case Rates among Those in Prison and General Population
+The closed and densely populated environment within prisons creates ideal conditions for the proliferation of large infectious diseases.
+The data stemming from the recent COVID-19 pandemic serves as a poignant illustration of this perspective, offering detailed insights into the heightened vulnerability of incarcerated populations to the rapid transmission and severe impact of contagious illnesses.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+The prison population stands out as a high-risk demographic group during the coronavirus disease 2019 (COVID-19) pandemic.
+In addition to residing in environments that are inherently challenging for practicing "social distancing," individuals within prisons often exhibit advanced age and possess multiple comorbidities.
+These characteristics are reflective of punitive policies that are discriminatory in nature and implemented worldwide (@elbek2020covid).
+
+According to the chart (@fig-planes), when comparing the overall new coronavirus infection rate among the American population with the new coronavirus infection rate among prison inmates, a clear trend emerges.
+In the majority of states in the United States, the data pertaining to infection rates among prison inmates surpasses that of the general population by a significant margin.
+
+\ The significant number of individuals held in incarceration across the United States, combined with prevalent environmental conditions within correctional facilities—such as overcrowding, limited sanitation, inadequate healthcare access, subpar ventilation, and challenges in maintaining social distancing—have presented distinct and substantial challenges and risks for both incarcerated individuals and staff members throughout the pandemic (@nowotny2020covid).
 

### 2024-02-11 outputs/paper/paper.qmd
change

@@
 
-According to the chart (@fig-planes), when comparing the overall new coronavirus infection rate among the American population with the new coronavirus infection rate among prison inmates, a clear trend emerges.
+When comparing the overall new coronavirus infection rate among the American population with the new coronavirus infection rate among prison inmates, a clear trend emerges according to the chart (@fig-planes).
 In the majority of states in the United States, the data pertaining to infection rates among prison inmates surpasses that of the general population by a significant margin.
@@
 \ The significant number of individuals held in incarceration across the United States, combined with prevalent environmental conditions within correctional facilities—such as overcrowding, limited sanitation, inadequate healthcare access, subpar ventilation, and challenges in maintaining social distancing—have presented distinct and substantial challenges and risks for both incarcerated individuals and staff members throughout the pandemic (@nowotny2020covid).
+
+\ @novisky2020institutional indicates that the implementation of varied epidemic prevention policies across different states in the United States, alongside differences in the infrastructure of state prisons, has resulted in significant disparities in prisoner infection rates.
 

### 2024-02-11 outputs/paper/paper.qmd
change

@@
 ```
+
+# Discussion
+
+## Cumulative COVID-19 Case Rates among Those in Prison and General Population
+The closed and densely populated environment within prisons creates ideal conditions for the proliferation of large infectious diseases.
+The data stemming from the recent COVID-19 pandemic serves as a poignant illustration of this perspective, offering detailed insights into the heightened vulnerability of incarcerated populations to the rapid transmission and severe impact of contagious illnesses.
+
+The prison population stands out as a high-risk demographic group during the coronavirus disease 2019 (COVID-19) pandemic.
+In addition to residing in environments that are inherently challenging for practicing "social distancing," individuals within prisons often exhibit advanced age and possess multiple comorbidities.
+These characteristics are reflective of punitive policies that are discriminatory in nature and implemented worldwide (@elbek2020covid).
+
+When comparing the overall new coronavirus infection rate among the American population with the new coronavirus infection rate among prison inmates, a clear trend emerges according to the chart (@fig-planes).
+In the majority of states in the United States, the data pertaining to infection rates among prison inmates surpasses that of the general population by a significant margin.
+
+\ The significant number of individuals held in incarceration across the United States, combined with prevalent environmental conditions within correctional facilities—such as overcrowding, limited sanitation, inadequate healthcare access, subpar ventilation, and challenges in maintaining social distancing—have presented distinct and substantial challenges and risks for both incarcerated individuals and staff members throughout the pandemic (@nowotny2020covid).
+
+\ @novisky2020institutional indicates that the implementation of varied epidemic prevention policies across different states in the United States, alongside differences in the infrastructure of state prisons, has resulted in significant disparities in prisoner infection rates.
+
+\ In addition to replicating the original data, we have incorporated a comparison of the COVID-19 infection rate among prison staff with the overall U.S.
+COVID-19 infection rate.
+According to the figure(@fig-staff), the infection rate among prison staff surpasses the overall infection rate but remains lower than the new coronavirus infection rate among incarcerated individuals, positioning it roughly in the middle between the two.
+This observation underscores the vulnerable position of prisoners within correctional facilities during the pandemic.
+
+## Weaknesses
+### Bias in Data Analysis
+On one hand, it's noteworthy that a considerable portion of data regarding U.S.
+prisons exclusively pertains to men, leading to the phenomenon referred to as "big dick data." This term underscores the prevalence of male-dominated datasets, which not only underscores systemic bias and marginalization, particularly towards women but also sheds light on existing power dynamics.
+The absence or marginalization of women in these datasets not only mirrors prevailing power structures but also perpetuates gender-based biases and stereotypes.
+Such gender disparity distorts our comprehension of reality, reinforces harmful stereotypes and inequalities, and presents substantial hurdles to data-driven decision-making (@dignazio2020data).
+
+\ On the other hand, when examining racial data, it tends to be categorized broadly into whites and blacks.
+This practice not only reinforces the binary opposition between these two racial groups in the United States but also overlooks the experiences of other ethnic minorities.
+
+### Measurement error
+Utilizing data from various origins, a practice known as data fusion or integration, introduces complexities and hurdles that can result in measurement inaccuracies.
+Each dataset carries its unique biases, constraints, and inaccuracies stemming from variations in data collection methods, sampling approaches, measurement tools, and processing methodologies.
+
+The amalgamation of data from disparate sources often introduces disparities in quality, consistency, and reliability, leading to inconsistencies or inaccuracies in the merged datasets.
+Moreover, issues like incomplete data, absent values, and misclassification errors can compound measurement inaccuracies.
+
+## future
+On the one hand, similar data collection, statistical analysis, and comparative studies of Canadian prisons provide an attractive avenue for gaining insights due to Canada's geographic proximity to the United States and some shared cultural and legal frameworks.
+This similarity in land area and certain social aspects may allow for more meaningful comparisons and broader conclusions.
+
+On the other hand, a comparison of prison data from smaller Nordic countries, represented by Iceland, gives a markedly different context.
+These countries tend to have very different social norms, legal frameworks, and approaches to criminal justice than North American countries.
+Factors such as smaller population sizes, different cultural attitudes toward crime and punishment, and alternative approaches to rehabilitation may contribute to contrasting prison data.
+
+Apart from large-scale studies, conducting small controlled experiments could offer valuable insights into the influence of different prison environments on the physical and mental well-being of inmates.
+
+Studying the experiences of prison staff can provide insight into challenges within correctional facilities and facilitate the development of effective policies.
+Likewise, exploring the impact of incarceration on families can provide greater insight into broader social impacts, including emotional distress and financial stress.
+Including their voices in research and policy discussions is critical to addressing the complex issues surrounding incarceration and reentry.
 
@@
 ```{r fig.height=10, fig.width=10}
-#| label: Bills of penguins
+#| label: fig-staff
 #| fig-cap: Cumulative COVID-19 Case Rates among Those in Prison Staff and General Population
@@
 
-# Discussion
-
-## Cumulative COVID-19 Case Rates among Those in Prison and General Population
-The closed and densely populated environment within prisons creates ideal conditions for the proliferation of large infectious diseases.
-The data stemming from the recent COVID-19 pandemic serves as a poignant illustration of this perspective, offering detailed insights into the heightened vulnerability of incarcerated populations to the rapid transmission and severe impact of contagious illnesses.
-
-The prison population stands out as a high-risk demographic group during the coronavirus disease 2019 (COVID-19) pandemic.
-In addition to residing in environments that are inherently challenging for practicing "social distancing," individuals within prisons often exhibit advanced age and possess multiple comorbidities.
-These characteristics are reflective of punitive policies that are discriminatory in nature and implemented worldwide (@elbek2020covid).
-
-When comparing the overall new coronavirus infection rate among the American population with the new coronavirus infection rate among prison inmates, a clear trend emerges according to the chart (@fig-planes).
-In the majority of states in the United States, the data pertaining to infection rates among prison inmates surpasses that of the general population by a significant margin.
-
-\ The significant number of individuals held in incarceration across the United States, combined with prevalent environmental conditions within correctional facilities—such as overcrowding, limited sanitation, inadequate healthcare access, subpar ventilation, and challenges in maintaining social distancing—have presented distinct and substantial challenges and risks for both incarcerated individuals and staff members throughout the pandemic (@nowotny2020covid).
-
-\ @novisky2020institutional indicates that the implementation of varied epidemic prevention policies across different states in the United States, alongside differences in the infrastructure of state prisons, has resulted in significant disparities in prisoner infection rates.
-
-## Second discussion point
-
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
-
 \newpage
@@
 
-## Diagnostics
-
 \newpage

### 2024-02-11 outputs/paper/paper.qmd
change

@@
 # Discussion
+## rehabilitating
+Rehabilitation refers to a series of interventions aimed at enhancing functioning and diminishing disability in individuals with health conditions, taking into account their interactions with the environment.Academics studying mass incarceration identify the 1970s as a critical juncture in U.S.
+penal history, characterized by a transition towards stricter punitive measures and a widespread belief that traditional rehabilitation methods were ineffective(@Rehabilitation).
 
-## Cumulative COVID-19 Case Rates among Those in Prison and General Population
-The closed and densely populated environment within prisons creates ideal conditions for the proliferation of large infectious diseases.
-The data stemming from the recent COVID-19 pandemic serves as a poignant illustration of this perspective, offering detailed insights into the heightened vulnerability of incarcerated populations to the rapid transmission and severe impact of contagious illnesses.
+The initial segment investigates prisoner engagement in rehabilitation initiatives across the United States.
+@fig-admit delineates four program categories (drug rehabilitation, education, job training, employment) and four regional divisions (Northeast, Midwest, South, West).
+Preliminary findings indicate that participation rates in the Northeast region tend to surpass those in the other three regions overall, whereas participation in the West region appears consistently lower across all four projects.
+Participation levels in the Southern region exhibit significant year-to-year fluctuations.
 
-The prison population stands out as a high-risk demographic group during the coronavirus disease 2019 (COVID-19) pandemic.
-In addition to residing in environments that are inherently challenging for practicing "social distancing," individuals within prisons often exhibit advanced age and possess multiple comorbidities.
-These characteristics are reflective of punitive policies that are discriminatory in nature and implemented worldwide (@elbek2020covid).
-
-When comparing the overall new coronavirus infection rate among the American population with the new coronavirus infection rate among prison inmates, a clear trend emerges according to the chart (@fig-planes).
-In the majority of states in the United States, the data pertaining to infection rates among prison inmates surpasses that of the general population by a significant margin.
-
-\ The significant number of individuals held in incarceration across the United States, combined with prevalent environmental conditions within correctional facilities—such as overcrowding, limited sanitation, inadequate healthcare access, subpar ventilation, and challenges in maintaining social distancing—have presented distinct and substantial challenges and risks for both incarcerated individuals and staff members throughout the pandemic (@nowotny2020covid).
-
-\ @novisky2020institutional indicates that the implementation of varied epidemic prevention policies across different states in the United States, alongside differences in the infrastructure of state prisons, has resulted in significant disparities in prisoner infection rates.
-
-\ In addition to replicating the original data, we have incorporated a comparison of the COVID-19 infection rate among prison staff with the overall U.S.
-COVID-19 infection rate.
-According to the figure(@fig-staff), the infection rate among prison staff surpasses the overall infection rate but remains lower than the new coronavirus infection rate among incarcerated individuals, positioning it roughly in the middle between the two.
-This observation underscores the vulnerable position of prisoners within correctional facilities during the pandemic.
-
-## Weaknesses
-### Bias in Data Analysis
-On one hand, it's noteworthy that a considerable portion of data regarding U.S.
-prisons exclusively pertains to men, leading to the phenomenon referred to as "big dick data." This term underscores the prevalence of male-dominated datasets, which not only underscores systemic bias and marginalization, particularly towards women but also sheds light on existing power dynamics.
-The absence or marginalization of women in these datasets not only mirrors prevailing power structures but also perpetuates gender-based biases and stereotypes.
-Such gender disparity distorts our comprehension of reality, reinforces harmful stereotypes and inequalities, and presents substantial hurdles to data-driven decision-making (@dignazio2020data).
-
-\ On the other hand, when examining racial data, it tends to be categorized broadly into whites and blacks.
-This practice not only reinforces the binary opposition between these two racial groups in the United States but also overlooks the experiences of other ethnic minorities.
-
-### Measurement error
-Utilizing data from various origins, a practice known as data fusion or integration, introduces complexities and hurdles that can result in measurement inaccuracies.
-Each dataset carries its unique biases, constraints, and inaccuracies stemming from variations in data collection methods, sampling approaches, measurement tools, and processing methodologies.
-
-The amalgamation of data from disparate sources often introduces disparities in quality, consistency, and reliability, leading to inconsistencies or inaccuracies in the merged datasets.
-Moreover, issues like incomplete data, absent values, and misclassification errors can compound measurement inaccuracies.
-
-## future
-On the one hand, similar data collection, statistical analysis, and comparative studies of Canadian prisons provide an attractive avenue for gaining insights due to Canada's geographic proximity to the United States and some shared cultural and legal frameworks.
-This similarity in land area and certain social aspects may allow for more meaningful comparisons and broader conclusions.
-
-On the other hand, a comparison of prison data from smaller Nordic countries, represented by Iceland, gives a markedly different context.
-These countries tend to have very different social norms, legal frameworks, and approaches to criminal justice than North American countries.
-Factors such as smaller population sizes, different cultural attitudes toward crime and punishment, and alternative approaches to rehabilitation may contribute to contrasting prison data.
-
-Apart from large-scale studies, conducting small controlled experiments could offer valuable insights into the influence of different prison environments on the physical and mental well-being of inmates.
-
-Studying the experiences of prison staff can provide insight into challenges within correctional facilities and facilitate the development of effective policies.
-Likewise, exploring the impact of incarceration on families can provide greater insight into broader social impacts, including emotional distress and financial stress.
-Including their voices in research and policy discussions is critical to addressing the complex issues surrounding incarceration and reentry.
+The processed data only provides a rough division of the United States into four major regions based on geographical location, limiting the possibility of conducting more detailed data analysis.
+Unfortunately, the original author only briefly mentioned the data source without elaborating on the data processing methods.
+Moreover, due to the large size of the original dataset, extracting more detailed variable classification data proved to be challenging.
 
@@
 ```
+The original data table exclusively focused on a subset of admitted individuals for the analysis of the American Prison Rehabilitation Program.
+Consequently, we opted to select the not admitted portion of the dataset to create similar charts for comparative analysis.
+@fig-plane illustrates that there is minimal disparity between the two groups regarding participation in drug rehabilitation and employment programs.
+However, the non-admitted group exhibits higher participation rates in education and vocational training initiatives.
 
+There is increasing evidence suggesting that in certain instances, incarceration can facilitate prisoners' reintegration into society (@arbour2021prison).
+Therefore, it may be beneficial for the U.S.
+government to implement additional programs aimed at assisting prisoners in readjusting to society.
+This approach not only reflects a commitment to humanistic values but also serves to bolster social security and foster broader societal development.
+
+## Cumulative COVID-19 Case Rates among Those in Prison and General Population
+The closed and densely populated environment within prisons creates ideal conditions for the proliferation of large infectious diseases.
+The data stemming from the recent COVID-19 pandemic serves as a poignant illustration of this perspective, offering detailed insights into the heightened vulnerability of incarcerated populations to the rapid transmission and severe impact of contagious illnesses.
+
+The prison population stands out as a high-risk demographic group during the coronavirus disease 2019 (COVID-19) pandemic.
+In addition to residing in environments that are inherently challenging for practicing "social distancing," individuals within prisons often exhibit advanced age and possess multiple comorbidities.
+These characteristics are reflective of punitive policies that are discriminatory in nature and implemented worldwide (@elbek2020covid).
+
+When comparing the overall new coronavirus infection rate among the American population with the new coronavirus infection rate among prison inmates, a clear trend emerges according to the chart (@fig-planes).
+In the majority of states in the United States, the data pertaining to infection rates among prison inmates surpasses that of the general population by a significant margin.
+
+\ The significant number of individuals held in incarceration across the United States, combined with prevalent environmental conditions within correctional facilities—such as overcrowding, limited sanitation, inadequate healthcare access, subpar ventilation, and challenges in maintaining social distancing—have presented distinct and substantial challenges and risks for both incarcerated individuals and staff members throughout the pandemic (@nowotny2020covid).
+
+\ @novisky2020institutional indicates that the implementation of varied epidemic prevention policies across different states in the United States, alongside differences in the infrastructure of state prisons, has resulted in significant disparities in prisoner infection rates.
+
+\ In addition to replicating the original data, we have incorporated a comparison of the COVID-19 infection rate among prison staff with the overall U.S.
+COVID-19 infection rate.
+According to the figure(@fig-staff), the infection rate among prison staff surpasses the overall infection rate but remains lower than the new coronavirus infection rate among incarcerated individuals, positioning it roughly in the middle between the two.
+This observation underscores the vulnerable position of prisoners within correctional facilities during the pandemic.
 ```{r fig.height=10, fig.width=10 }
@@
 
+## Weaknesses
+### Bias in Data Analysis
+On one hand, it's noteworthy that a considerable portion of data regarding U.S.
+prisons exclusively pertains to men, leading to the phenomenon referred to as "big dick data." This term underscores the prevalence of male-dominated datasets, which not only underscores systemic bias and marginalization, particularly towards women but also sheds light on existing power dynamics.
+The absence or marginalization of women in these datasets not only mirrors prevailing power structures but also perpetuates gender-based biases and stereotypes.
+Such gender disparity distorts our comprehension of reality, reinforces harmful stereotypes and inequalities, and presents substantial hurdles to data-driven decision-making (@dignazio2020data).
+
+\ On the other hand, when examining racial data, it tends to be categorized broadly into whites and blacks.
+This practice not only reinforces the binary opposition between these two racial groups in the United States but also overlooks the experiences of other ethnic minorities.
+
+### Measurement error
+Utilizing data from various origins, a practice known as data fusion or integration, introduces complexities and hurdles that can result in measurement inaccuracies.
+Each dataset carries its unique biases, constraints, and inaccuracies stemming from variations in data collection methods, sampling approaches, measurement tools, and processing methodologies.
+
+The amalgamation of data from disparate sources often introduces disparities in quality, consistency, and reliability, leading to inconsistencies or inaccuracies in the merged datasets.
+Moreover, issues like incomplete data, absent values, and misclassification errors can compound measurement inaccuracies.
+
+## future
+On the one hand, similar data collection, statistical analysis, and comparative studies of Canadian prisons provide an attractive avenue for gaining insights due to Canada's geographic proximity to the United States and some shared cultural and legal frameworks.
+This similarity in land area and certain social aspects may allow for more meaningful comparisons and broader conclusions.
+
+On the other hand, a comparison of prison data from smaller Nordic countries, represented by Iceland, gives a markedly different context.
+These countries tend to have very different social norms, legal frameworks, and approaches to criminal justice than North American countries.
+Factors such as smaller population sizes, different cultural attitudes toward crime and punishment, and alternative approaches to rehabilitation may contribute to contrasting prison data.
+
+Apart from large-scale studies, conducting small controlled experiments could offer valuable insights into the influence of different prison environments on the physical and mental well-being of inmates.
+
+Studying the experiences of prison staff can provide insight into challenges within correctional facilities and facilitate the development of effective policies.
+Likewise, exploring the impact of incarceration on families can provide greater insight into broader social impacts, including emotional distress and financial stress.
+Including their voices in research and policy discussions is critical to addressing the complex issues surrounding incarceration and reentry.
+
 \newpage

### 2024-02-12 scripts/00-simulate_data.R
update "test_data.R"

@@ -10,10 +10,31 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Simulate data ####
 # [...ADD CODE HERE...]
+# Set seed for reproducibility
+set.seed(123)
+
+# Generate example data for 20 countries
+countries <- paste("Country", 1:20)
+prison_populations <- sample(1000:10000, 20, replace = TRUE)  # Example prison populations
+national_populations <- sample(500000:5000000, 20, replace = TRUE)  # Example national populations
+
+# Calculate prison population rates per 100,000
+prison_rates <- (prison_populations / national_populations) * 100000
+
+# Create a data frame to store the simulated data
+simulated_data <- data.frame(
+  Country = countries,
+  Prison_Population = prison_populations,
+  National_Population = national_populations,
+  Prison_Rate_per_100000 = prison_rates
+)
+
+# Print the simulated data
+head(simulated_data)
 
 
 

### 2024-02-12 scripts/03-test_data.R

@@ -13,3 +13,47 @@ library(tidyverse)
 # [...UPDATE THIS...]
 
 #### Test data ####
+set.seed(123)
+
+# Generate example data for 20 countries
+countries <- paste("Country", 1:20)
+prison_populations <- sample(1000:10000, 20, replace = TRUE)  # Example prison populations
+national_populations <- sample(500000:5000000, 20, replace = TRUE)  # Example national populations
+
+# Calculate prison population rates per 100,000
+prison_rates <- (prison_populations / national_populations) * 100000
+
+# Create a data frame to store the simulated data
+simulated_data <- data.frame(
+  Country = countries,
+  Prison_Population = prison_populations,
+  National_Population = national_populations,
+  Prison_Rate_per_100000 = prison_rates
+)
+
+test_that("Data frame has the correct dimensions", {
+  expect_equal(nrow(simulated_data), 20)
+  expect_equal(ncol(simulated_data), 4)
+})
+
+test_that("Data frame contains required columns", {
+  expect_true("Country" %in% names(simulated_data))
+  expect_true("Prison_Population" %in% names(simulated_data))
+  expect_true("National_Population" %in% names(simulated_data))
+  expect_true("Prison_Rate_per_100000" %in% names(simulated_data))
+})
+
+test_that("Prison_Population and National_Population have valid values", {
+  expect_true(all(simulated_data$Prison_Population >= 1000))
+  expect_true(all(simulated_data$Prison_Population <= 10000))
+  expect_true(all(simulated_data$National_Population >= 500000))
+  expect_true(all(simulated_data$National_Population <= 5000000))
+})
+
+test_that("Prison_Rate_per_100000 falls within a reasonable range", {
+  expect_true(all(simulated_data$Prison_Rate_per_100000 >= 0))
+  expect_true(all(simulated_data$Prison_Rate_per_100000 <= 2000))  # A typical upper limit for prison rates
+})
+test_that("Country names are unique", {
+  expect_true(length(unique(simulated_data$Country)) == nrow(simulated_data))
+})

### 2024-02-12 scripts/02-data_cleaning.R
update"test_data.R"

@@ -10,20 +10,20 @@
 #### Workspace setup ####
 library(tidyverse)
 
-#### Clean data ####
+
+# Read in the raw data from the CSV file
 raw_data <- read_csv("inputs/data/country_data.csv")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(title, prison_population_rate) |>
-  filter(title%in% c ("United States of America","Croatia","United Kingdom: England & Wales","Spain",
-                         "France","Austria", "Italy","Belgium","Switzerland",
-                      "Ireland", "Germany" ,"Denmark" ,"Norway","Netherlands", "Sweden",
-                      "Finland","Egypt","Canada","Norway","Singapore","Japan","Iceland"))|>
-rename(country=title)
+# Clean the data
+cleaned_data <- 
+  raw_data |>  # Pipe operator for cleaner syntax
+  janitor::clean_names() |>  # Clean column names
+  select(title, prison_population_rate) |>  # Select only relevant columns
+  filter(title %in% c ("United States of America","Croatia","United Kingdom: England & Wales","Spain",
+                       "France","Austria", "Italy","Belgium","Switzerland",
+                       "Ireland", "Germany" ,"Denmark" ,"Norway","Netherlands", "Sweden",
+                       "Finland","Egypt","Canada","Norway","Singapore","Japan","Iceland")) |>  # Filter specific countries
+  rename(country = title)  # Rename 'title' column to 'country'
 
- 
-
-#### Save data ####
+# Save the cleaned data to a new CSV file
 write_csv(cleaned_data, "outputs/data/clean_country_data.csv")

### 2024-02-13 outputs/paper/paper.qmd
update

@@
 ## Source
-The paper used for replication is "Inside the Box: Safety, Health, and Isolation in Prison," which mainly analyzes the impact of prisons on safety and health, and specifically includes data from the new coronavirus pandemic.
+The paper used for replication is Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside), which mainly analyzes the impact of prisons on safety and health, and specifically includes data from the new coronavirus pandemic.
 
-Sourcebook of Criminal Justice Statistics, Bureau of Justice Statistics Report, Jail Inmates in 2018, U.S. Population FRED Data, World Prison Population Data, and Western B. and Pettit B data
+Sourcebook of Criminal Justice Statistics
+\ Bureau of Justice Statistics Report   
+Jail Inmates in 2018, U.S. Population FRED Data  
+World Prison Population Data   
+Western B. and Pettit B data
+\ Survey of Inmates of States Correctional Facilities (1986, 1991, 1997, 2004)
+\ Survey of Prison Inmates (2016) (Bureau of Justice Statistics 1994, 2004a, 2004b, 2006, 2019, 2021)
 
@@
 
- mass incarceration.xlsx
-
- incarceration 1925-2019
+## data cleaning and construction
+Accurate data cleansing and structuring are paramount in research.
+Given the extensive and varied raw data analyzed in the original paper Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside) and the lack of detailed explanation regarding data processing methods by the original author, Figures 1, 2, 4, 5, 6, and 7 are derived from processed data provided by the original author, albeit with a distinct focus in visualization.
+For figure 2, we obtained the updated version of the original data and expanded it by incorporating data from an additional 5 countries to enhance comprehensiveness.
 
@@
 Original data comes from two prison questionnaires
-For example, the sample for the 2004 survey was drawn from two different documents.
+\ For example, the sample for the 2004 survey was drawn from two different documents.
 The primary archive includes a list of 1,549 state prisons from the June 30, 2000, BJS 2000 Census of State and Federal Correctional Facilities.
@@
 ```
-## Comparing
+```{r fig.height=6, fig.width=6 }
+#| label: fig-men
+#| fig-cap: Men’s cumulative imprisonment risk, by cohort
+#| echo: false
+#| warning: false
+#| message: false
+
+library(openxlsx)
+
+file_path <- here::here("inputs/data/mass incarceration.xlsx")
+
+# Read the Excel file
+
+data <- read.xlsx(file_path, sheet = 3)
+data <- data %>%
+  mutate(
+    race = case_when(
+      race == "W" ~ "White",
+      race == "B" ~ "Black",
+      TRUE ~ race
+    ),
+    cohort = case_when(
+      cohort == "45-49" ~ "Born 1945-1949",
+      cohort == "75-79" ~ "Born 1975-1979",
+      TRUE ~ cohort
+    )
+  )
+ggplot(data, aes(x = race, y = risk, fill = education)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  facet_wrap(~cohort) +
+  labs(
+       x = "Race",
+       y = "Risk",
+       fill = "Education") +
+  theme_minimal()
+
+```
+
+## Exploring Racial Disparities in Incarceration Trends
+Despite extensive discussions surrounding the surge in the U.S.
+prison population over the last twenty-five years (@pettit2004mass), scant attention has been paid to the evolution of incarceration inequality.
+Our study delves into sentencing disparities by analyzing the likelihood of incarceration among blacks and whites across varying educational attainment levels.
+The data(@fig-men) reveals stark contrasts: irrespective of educational achievement, black individuals face significantly higher incarceration rates compared to their white counterparts, particularly among those with less than twelve years of schooling.
+
+## Global Perspectives on Mass Incarceration
 In addition to examining the trajectory of incarceration rates within the United States over time, it is equally imperative to conduct horizontal comparisons by scrutinizing incarceration rates across different countries.
@@
 #| label: fig-country
-#| fig-cap: Relationship between wing length and width
+#| fig-cap: Prison Population Rate by Country
 #| echo: false
@@
   theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5)) +  # Rotate x-axis labels
-  labs(x = "Prison Population Rate", y = "country") +  # Add axis labels
-  ggtitle("Prison Population Rate by Country ")  # Add title
+  labs(x = "Prison Population Rate", y = "country")  # Add axis labels
 
@@
 #| label: fig-admit
-#| fig-cap: Relationship between wing length and width
+#| fig-cap: Enrollment in Drug, Education, Job Training Programs, and Work Assignment, State Prisoners, by Region_admit
 #| echo: false
@@
 #| label: fig-plane
-#| fig-cap: Relationship between wing length and width
+#| fig-cap: Enrollment in Drug, Education, Job Training Programs, and Work Assignment, State Prisoners, by Region_not_admit
 #| echo: false

### 2024-02-13 outputs/paper/paper.qmd
upadte

@@
 ---
-title: "Delving into the World Inside Prisons for Safety, Health, and Isolation"
+title: "Exploring the World Inside US Prisons for Safety, Health, and Isolation"
 
@@
 #| label: fig-planes
-#| fig-cap: Cumulative COVID-19 Case Rates among Those in Prison and General Population, by State
+#| fig-cap: Cumulative COVID-19 Case Rates among Those in Imprisoned persons and General Population, by State
 #| echo: false

### 2024-02-13 outputs/paper/paper.qmd
add the "Table of Contents"

@@
 date-format: long
-abstract: "This social science research focuses on the impact of prisons on crime rates and socioeconomic disparities.
-However, the penal institutions are often disregarded, creating a significant gap in understanding its true effect.
-This paper takes a look at the prison, their function in rehabilitation efforts, their role as setting for violence, healthcare provision, and the isolation experienced in solitary confinement.
-Recent studies indicate that fewer inmates are involved in programs now compared to the 1980’s, and prisoners face more violence, sickness, and isolation.
-These conditions question if prisons are really treating people with dignity and respect, and how these acts will affect people who recently joined the society again.
+abstract: "This study replicates and extends research on prison safety, health, and COVID-19 impact, revealing stark disparities in incarceration rates between black and white individuals, especially among those with lower education levels.
+The findings underscore the persistent issue of mass incarceration in the United States and the urgent need for comprehensive strategies to address inequalities within the criminal justice system.
+Understanding these disparities is crucial for fostering a more equitable society and improving outcomes for marginalized populations.
 "
 format: pdf
+toc: true
 number-sections: true
@@
 
-This paper explores how prisons impact crime and inequality.
-Prisons are often overlooked compared to other institutions such as schools or hospitals.
-We are focusing on the US, where the concept of “mass incarceration” is a big issue, in other words there are a lot of people in prison, especially Black men with limited education.
-This mostly happens due to strict laws against Black men and inequality that rise upon the issue.
-Researchers have studied incarceration in various angles, examining its effects on how prisons affect crime rates, labor markets, health outcomes, and family dynamics.
-Despite debates over rehabilitation, it is still hard for them to get jobs and be accepted in society.
-This paper takes a unique perspective, where we view US penal institutions as “total institutions” where individuals face constricted control and minimal autonomy.
-We are exploring key issues such as overcrowding, violence, health challenges, and the harsh realities of solitary confinement.
-By understanding what happens inside prisons, we can gain a deeper understanding of the problems of mass incarceration and work towards making things better.
-→ We can add details after we decide what data and model we are going to use (Ex. Rate has increased 80% over 1990 to 2020)
+This paper delves into the profound impacts of prisons on safety and health for incarcerated individuals, shedding light on an often overlooked facet of society compared to institutions like schools or hospitals.
+Focusing on the United States, where the concept of "mass incarceration" looms large, we observe a staggering increase in the prison population since the 1970s, despite a slight decline in recent years.
+Notably, Black men with limited education face disproportionate rates of incarceration, reflecting systemic inequalities in the justice system.
+The study examines various aspects of incarceration, including its effects on crime rates, labor markets, and family dynamics, revealing persistent challenges in prisoner rehabilitation and societal reintegration.
 
-The remainder of this paper is structured as follows. @sec-data....
+Furthermore, this paper offers a unique perspective on US penal institutions as 'total institutions,' where inmates experience stringent control and minimal autonomy, leading to isolation and restricted freedom.
+Key issues such as mass incarceration, the COVID-19 pandemic, violence, health challenges, and the harsh realities of solitary confinement are explored, with a focus on the high prevalence of COVID-19 cases among prisoners.
+Global comparisons of mass incarceration trends across 20 countries provide insights into the broader context of prison systems worldwide.
+
+By comprehensively understanding the dynamics within prisons, this paper aims to contribute to the discourse on mass incarceration and advocate for positive reforms.
+Additionally, the paper replicates and builds upon Bruce Western's findings.Data cleaning and analysis were conducted using the open-source statistical programming language R (@citeR), leveraging functionalities from the tidyverse (@tidyverse) suite, including ggplot2 (@ggplot2), dplyr (@dplyr), readr (@readr), tibble (@tibble),stringr (@stringr) ,haven(@haven),openxlsx(@openxlsx),janitor (@janitor) and knitr (@knitr).
+The detailed procedures for data extraction and cleaning are expounded upon in the subsequent subsections.
+
+The remainder of this paper is structured as follows. @sec-data
 
@@
 
-## Features
-mass incarceration.xlsx
-
- incarceration 1925-2019
- Year:1925-2019
- Prison: integer number
- Prison rate per(100k) : easy to read and compare
- Jail
- Total
- Population
- Total Rate
-
- world incarceration rates
- rate
- rate18
-
- cumulative risk
- race :w(white) b(black) Lack of data on other ethnic minorities
-
- education
- cohort
- risk
-
-COVID-19 Cases in State and Federal Prison Systems.csv：
-Prison System
-Incarcerated Tested
-Incarcerated Positive,
-Incarcerated Deaths,
-Staff Positive,
-Staff Deaths,
-Incarcerated Case rate per 1,000
-Scrape Date
-Staff Case rate per 1,000
-state
-
-statepop.csv:
-sate
-abbreviation
-
-all-states-history.csv:
-
 ## Measurement:
@@
 Data was collected through face-to-face interviews with prisoners using computer-assisted personal interviewing techniques.
-
-Cumulative COVID-19 Case Rates among Those in Prison and General Population, by State: March 2020 to January 2021
 
@@
 
-\newpage
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-\newpage
-
 # References

### 2024-02-13 outputs/paper/paper.qmd
update

@@
 date-format: long
-abstract: "This study replicates and extends research on prison safety, health, and COVID-19 impact, revealing stark disparities in incarceration rates between black and white individuals, especially among those with lower education levels.
-The findings underscore the persistent issue of mass incarceration in the United States and the urgent need for comprehensive strategies to address inequalities within the criminal justice system.
-Understanding these disparities is crucial for fostering a more equitable society and improving outcomes for marginalized populations.
+abstract: "This study replicates and extends research on prison safety, health, and COVID-19 impact, finding significant disparities in incarceration rates between black and white individuals, particularly among those with lower education levels.
+The findings highlight the enduring issue of mass incarceration in the United States and emphasize the urgent need for comprehensive strategies to address inequalities within the criminal justice system.
+Understanding these disparities is critical for promoting a more equitable society and enhancing outcomes for marginalized populations.
 "
@@
 install.packages("openxlsx")
+install.packages("knitr")
+install.packages("kableExtra")
+library(kableExtra)
 library(openxlsx)
@@
 library(dplyr)
+library(knitr)
 ```
@@
 The study examines various aspects of incarceration, including its effects on crime rates, labor markets, and family dynamics, revealing persistent challenges in prisoner rehabilitation and societal reintegration.
-
 Furthermore, this paper offers a unique perspective on US penal institutions as 'total institutions,' where inmates experience stringent control and minimal autonomy, leading to isolation and restricted freedom.
@@
 Global comparisons of mass incarceration trends across 20 countries provide insights into the broader context of prison systems worldwide.
-
 By comprehensively understanding the dynamics within prisons, this paper aims to contribute to the discourse on mass incarceration and advocate for positive reforms.
-Additionally, the paper replicates and builds upon Bruce Western's findings.Data cleaning and analysis were conducted using the open-source statistical programming language R (@citeR), leveraging functionalities from the tidyverse (@tidyverse) suite, including ggplot2 (@ggplot2), dplyr (@dplyr), readr (@readr), tibble (@tibble),stringr (@stringr) ,haven(@haven),openxlsx(@openxlsx),janitor (@janitor) and knitr (@knitr).
+Additionally, the paper replicates and builds upon Bruce Western's findings.Data cleaning and analysis were conducted using the open-source statistical programming language `R`[@citeR], leveraging functionalities from the tidyverse (@tidyverse), ggplot2 (@ggplot2), dplyr (@dplyr), readr (@readr), tibble (@tibble),stringr (@stringr) ,haven(@haven),openxlsx(@openxlsx),janitor (@janitor) and knitr (@knitr).
 The detailed procedures for data extraction and cleaning are expounded upon in the subsequent subsections.
-
 The remainder of this paper is structured as follows. @sec-data
@@
 For figure 2, we obtained the updated version of the original data and expanded it by incorporating data from an additional 5 countries to enhance comprehensiveness.
+@tbl-country
 
-## Measurement:
+```{r }
+#| label: tbl-country
+#| echo: false
+#| eval: true
+#| warning: false
+#| tbl-cap: prison rates in 20 countries
+
+data <- read.csv(file = here::here("outputs/data/clean_country_data.csv"))
+kable(data, format = "markdown", booktabs = TRUE) %>%
+  kable_styling(full_width = FALSE) %>%
+  column_spec(1, border_left = TRUE) %>%
+  column_spec(2, border_right = TRUE)
+
+```
+
+## Measurement
 Enrollment in Drug, Education, Job Training Programs, and Work Assignment, State Prisoners, by Region
 Original data comes from two prison questionnaires    
-\ For example, the sample for the 2004 survey was drawn from two different documents.
+For example, the sample for the 2004 survey was drawn from two different documents.
 The primary archive includes a list of 1,549 state prisons from the June 30, 2000, BJS 2000 Census of State and Federal Correctional Facilities.

### 2024-02-13 scripts/00-simulate_data.R
update the top matter of the R files in scripts

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates example data for 20 countries including prison populations, national populations, and prison rates per 100,000 people.
+# Author: Sirui Tan 
+# Date: 8 February 2024 
+# Contact: sirui.tan@utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? NO
 
 
 #### Workspace setup ####
@@ -13,7 +13,6 @@ library(tidyverse)
 
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
 # Set seed for reproducibility
 set.seed(123)
 

### 2024-02-13 outputs/paper/paper.qmd
update

@@
 install.packages("kableExtra")
+install.packages("readxl")
+library(readxl)
 library(kableExtra)
 library(openxlsx)
-library(haven)  # Load the haven package
+library(haven)  
 library(tidyverse)
@@
 
-library(openxlsx)
+file_path <- here::here("inputs/data/mass incarceration.xlsx")
+x0 <- read.xlsx(file_path, sheet = 1)
 
-file_path <- here::here("inputs/data/mass incarceration.xlsx")
-
-# Read the Excel file
-x0 <- read.xlsx(file_path, sheet = 1)
 par(mfrow=c(3,1))
@@
      xlab="", ylab="Incarceration Rate (per 100,000)", lty=1, lwd=2)
-title(" US Incarceration, 1925-2018")
 lines(x0$Year, x0$TotalRate, lty=2, col="red", lwd=2)
@@
 ```
+
 ```{r fig.height=6, fig.width=6 }
@@
 
-library(openxlsx)
-
 file_path <- here::here("inputs/data/mass incarceration.xlsx")
@@
 
-data <- read.xlsx(file_path, sheet = 3)
-data <- data %>%
+men_data <- read.xlsx(file_path, sheet = 3)
+men_data <- men_data %>%
   mutate(
@@
   )
-ggplot(data, aes(x = race, y = risk, fill = education)) +
+ggplot(men_data, aes(x = race, y = risk, fill = education)) +
   geom_bar(stat = "identity", position = "dodge") +
@@
 
-data <-  read.csv(file = here::here("outputs/data/clean_country_data.csv"))
+c_data <-  read.csv(file = here::here("outputs/data/clean_country_data.csv"))
 
-data <- data[order(-data$prison_population_rate), ]
+c_data <- data[order(-data$prison_population_rate), ]
 
 # Create the bar plot
-plot <- ggplot(data, aes(x =prison_population_rate, y = country)) +
+plot <- ggplot(c_data, aes(x =prison_population_rate, y = country)) +
   geom_bar(stat = "identity", fill = "skyblue") +
@@
 
-data_1 <- read_dta('../../inputs/data/spi86to16.dta')
+data_3 <- read_dta('../../inputs/data/spi86to16.dta')
 
-x <- data_1[data_1$admit==1,]
+x <- data_3[data_3$admit==1,]
 

### 2024-02-13 scripts/01-download_data.R

@@ -7,17 +7,12 @@
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]
 
-
 #### Workspace setup ####
-library(opendatatoronto)
+library(rvest)
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
-
-# Load required library
-library(rvest)
 
 # Define the URL of the webpage
 url <- "https://www.prisonstudies.org/highest-to-lowest/prison_population_rate?field_region_taxonomy_tid=All"
@@ -26,10 +21,7 @@ url <- "https://www.prisonstudies.org/highest-to-lowest/prison_population_rate?f
 page <- read_html(url)
 
 # Extract the table containing the data
-table_data <- html_table(page)[[1]]  # Assuming the data is in the first table
-
-# Save the data to a CSV file
-
+table_data <- html_table(page)[[1]]  
 
 #### Save data ####
 

### 2024-02-13 scripts/03-test_data.R

@@ -10,7 +10,7 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Test data ####
 set.seed(123)

### 2024-02-13 scripts/05-replicate.R

@@ -1,0 +1,268 @@
+#### Preamble ####
+# Purpose: Paper Replication
+# Author: Sirui Tan
+# Date: 11 February 2024 
+# Contact: sirui.tan@mail.utoronto.ca
+# License: MIT
+
+#### Workspace setup ####
+install.packages("readr")
+library(tidyverse)
+library(rvest)
+library(readxl)
+library(knitr)
+library(janitor)
+library(lubridate)
+library(dplyr)
+library(ggpubr)
+library(scales)
+library(here)
+library(kableExtra)
+library(openxlsx)
+library(haven) 
+
+#### Reading data ####
+
+url <- "https://www.prisonstudies.org/highest-to-lowest/prison_population_rate?field_region_taxonomy_tid=All"
+page <- read_html(url)
+table_data <- html_table(page)[[1]] 
+write_csv(table_data, "inputs/data/country_data.csv") 
+
+file_path <- here::here("inputs/data/mass incarceration.xlsx")
+x0 <- read.xlsx(file_path, sheet = 1)
+
+file_path_2 <- here::here("inputs/data/mass incarceration.xlsx")
+men_data <- read.xlsx(file_path_2, sheet = 3)
+
+admit_data <- read_dta(file = here::here("inputs/data/spi86to16.dta"))
+
+
+#### Cleaning data ####
+raw_data <- read_csv("inputs/data/country_data.csv")
+cleaned_data <- 
+  raw_data |>  # Pipe operator for cleaner syntax
+  janitor::clean_names() |>  # Clean column names
+  select(title, prison_population_rate) |>  # Select only relevant columns
+  filter(title %in% c ("United States of America","Croatia","United Kingdom: England & Wales","Spain",
+                       "France","Austria", "Italy","Belgium","Switzerland",
+                       "Ireland", "Germany" ,"Denmark" ,"Norway","Netherlands", "Sweden",
+                       "Finland","Egypt","Canada","Norway","Singapore","Japan","Iceland")) |>  # Filter specific countries
+  rename(country = title)  # Rename 'title' column to 'country'
+
[…]

### 2024-02-13 scripts/05-replicate.R
update

@@ -20,6 +20,7 @@ library(here)
 library(kableExtra)
 library(openxlsx)
 library(haven) 
+library(readr) 
 
 #### Reading data ####
 
@@ -69,7 +70,7 @@ abline(h=seq(0, 800, 200), v=seq(1920,2020,20), lty=3, col="gray")
 
 # Save the plot to a file
 png("outputs/graphs/US_incarceration_1925−2018.png", width = 10, height = 6)
-dev.off()
+
 
 
 ## CREATE FIGURE 2
@@ -107,13 +108,12 @@ plot <- ggplot(c_data, aes(x =prison_population_rate, y = country)) +
   theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5)) +  # Rotate x-axis labels
   labs(x = "Prison Population Rate", y = "country")  # Add axis labels
 # Save the plot to a file
+ggsave(filename = "outputs/graphs/Prison_population_rate_by_country.png",  width = 10, height = 6)
 
 
 ## CREATE FIGURE 4
 
-
-
-# Create the bar plot
+# Creating the figure
 
 x <- admit_data[admit_data$admit==1,] 
 
@@ -129,82 +129,7 @@ edev    <- data.matrix(edev[!is.nan(edev[,3]),])
 dimnames(drugev) <- dimnames(vocev) <- dimnames(work) <- dimnames(edev) <-
   list(NULL, c("region","year","xbar"))
 
-pdf("programs.pdf",height=6, width=8)
-par(mfrow=c(1,4))
-par(fig=c(0,.29, 0,1))
-plot(drugev[drugev[,"region"]==1,"year"],
-     drugev[drugev[,"region"]==1,"xbar"]*100,
-     type="b", pch=16, main="Drug Program",
-     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
-     axes=F, ylab="Percent", xlab="")
-axis(1)
-axis(2)
-lines(drugev[drugev[,"region"]==2,"year"], drugev[drugev[,"region"]==2,"xbar"]*100,
-      type="b", pch=17, col="dodgerblue")
-lines(drugev[drugev[,"region"]==3,"year"], drugev[drugev[,"region"]==3,"xbar"]*100,
-      type="b", pch=18, col="red")
-lines(drugev[drugev[,"region"]==4,"year"], drugev[drugev[,"region"]==4,"xbar"]*100,
[…]

### 2024-02-14 outputs/paper/paper.qmd
update the test_data

@@
 By comprehensively understanding the dynamics within prisons, this paper aims to contribute to the discourse on mass incarceration and advocate for positive reforms.
-Additionally, the paper replicates and builds upon Bruce Western's findings.Data cleaning and analysis were conducted using the open-source statistical programming language `R`[@citeR], leveraging functionalities from the tidyverse (@tidyverse), ggplot2 (@ggplot2), dplyr (@dplyr), readr (@readr), tibble (@tibble),stringr (@stringr) ,haven(@haven),openxlsx(@openxlsx),janitor (@janitor) and knitr (@knitr).
-The detailed procedures for data extraction and cleaning are expounded upon in the subsequent subsections.
-The remainder of this paper is structured as follows. @sec-data
+Additionally, the paper replicates and builds upon Bruce Western's findings.Data cleaning and analysis were conducted using the open-source statistical programming language `R`[@citeR], leveraging functionalities from the `tidyverse`[@tidyverse]，`ggplot2`[@ggplot2],`dplyr`[@dplyr],`readr`[@readr],`tibble`[@tibble],`stringr`[@stringr],`haven`[@haven],`openxlsx`[@openxlsx],`janitor`[@janitor],`knitr`[@knitr].
+The detailed procedures for data extraction and cleaning are expounded upon in the subsequent subsections(@sec-data).
 
@@
 ## Source
-The paper used for replication is Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside), which mainly analyzes the impact of prisons on safety and health, and specifically includes data from the new coronavirus pandemic.
+The paper used for replication is Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside), which mainly analyzes the impact of prisons on safety and health, and
+specifically includes data from the new coronavirus pandemic.
 
 Sourcebook of Criminal Justice Statistics   
-\ Bureau of Justice Statistics Report      
+Bureau of Justice Statistics Report      
 Jail Inmates in 2018, U.S. Population FRED Data     
@@
 Western B. and Pettit B data      
-\ Survey of Inmates of States Correctional Facilities (1986, 1991, 1997, 2004)   
-\ Survey of Prison Inmates (2016) (Bureau of Justice Statistics 1994, 2004a, 2004b, 2006, 2019, 2021)
+Survey of Inmates of States Correctional Facilities (1986, 1991, 1997, 2004)    
+Survey of Prison Inmates (2016) (Bureau of Justice Statistics 1994, 2004a, 2004b, 2006, 2019, 2021)
 
@@
 ## Measurement
-Enrollment in Drug, Education, Job Training Programs, and Work Assignment, State Prisoners, by Region
-Original data comes from two prison questionnaires    
+For @fig-over
+The Bureau of Justice Statistics (BJS) conducts thorough data collection and analysis on the populations incarcerated in both state and federal prisons, as well as local jails, across the United States.
+Utilizing diverse sources such as surveys, administrative records, and inmate censuses, BJS produces precise estimates of the total number of individuals held in correctional facilities.
+For @fig-admit and @fig-plane,original data comes from two prison questionnaires    
 For example, the sample for the 2004 survey was drawn from two different documents.
@@
 file_path <- here::here("inputs/data/mass incarceration.xlsx")
-
 # Read the Excel file
-
 men_data <- read.xlsx(file_path, sheet = 3)

### 2024-02-14 scripts/00-simulate_data.R

@@ -36,4 +36,32 @@ simulated_data <- data.frame(
 head(simulated_data)
 
 
+#### Test data ####
+
+test_that("Data frame has the correct dimensions", {
+  expect_equal(nrow(simulated_data), 20)
+  expect_equal(ncol(simulated_data), 4)
+})
+
+test_that("Data frame contains required columns", {
+  expect_true("Country" %in% names(simulated_data))
+  expect_true("Prison_Population" %in% names(simulated_data))
+  expect_true("National_Population" %in% names(simulated_data))
+  expect_true("Prison_Rate_per_100000" %in% names(simulated_data))
+})
+
+test_that("Prison_Population and National_Population have valid values", {
+  expect_true(all(simulated_data$Prison_Population >= 1000))
+  expect_true(all(simulated_data$Prison_Population <= 10000))
+  expect_true(all(simulated_data$National_Population >= 500000))
+  expect_true(all(simulated_data$National_Population <= 5000000))
+})
+
+test_that("Prison_Rate_per_100000 falls within a reasonable range", {
+  expect_true(all(simulated_data$Prison_Rate_per_100000 >= 0))
+  expect_true(all(simulated_data$Prison_Rate_per_100000 <= 2000))  # A typical upper limit for prison rates
+})
+test_that("Country names are unique", {
+  expect_true(length(unique(simulated_data$Country)) == nrow(simulated_data))
+})
 

### 2024-02-14 scripts/03-test_data.R

@@ -1,59 +1,47 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the real data
+# Author: Sirui Tan
+# Date: 14 February 2024 
+# Contact: sirui.tan@utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 
 #### Workspace setup ####
+
 library(tidyverse)
+library(readxl)
 
 
-#### Test data ####
-set.seed(123)
+#### Test real_data_1 ####
+file_path <- here::here("inputs/data/mass incarceration.xlsx")
+real_data_1 <- read.xlsx(file_path, sheet = 1)
 
-# Generate example data for 20 countries
-countries <- paste("Country", 1:20)
-prison_populations <- sample(1000:10000, 20, replace = TRUE)  # Example prison populations
-national_populations <- sample(500000:5000000, 20, replace = TRUE)  # Example national populations
+# Check if min year is 1925
+min_year_check <- min(real_data_1$Year) == 1925
 
-# Calculate prison population rates per 100,000
-prison_rates <- (prison_populations / national_populations) * 100000
+# Check if max year is 2019
+max_year_check <- max(real_data_1$Year) == 2019
 
-# Create a data frame to store the simulated data
-simulated_data <- data.frame(
-  Country = countries,
-  Prison_Population = prison_populations,
-  National_Population = national_populations,
-  Prison_Rate_per_100000 = prison_rates
-)
+# Check if min prison rate is >= 0
+min_prison_rate_check <- min(real_data_1$Prison.Rate.per.100k) >= 0
 
-test_that("Data frame has the correct dimensions", {
-  expect_equal(nrow(simulated_data), 20)
-  expect_equal(ncol(simulated_data), 4)
-})
+# Print the test results
+cat("Minimum year is 1925:", min_year_check, "\n")
+cat("Maximum year is 2019:", max_year_check, "\n")
+cat("Minimum prison rate is >= 0:", min_prison_rate_check, "\n")
 
-test_that("Data frame contains required columns", {
-  expect_true("Country" %in% names(simulated_data))
[…]

### 2024-02-15 outputs/paper/paper.qmd
add something in introduction

@@
 
-This paper delves into the profound impacts of prisons on safety and health for incarcerated individuals, shedding light on an often overlooked facet of society compared to institutions like schools or hospitals.
-Focusing on the United States, where the concept of "mass incarceration" looms large, we observe a staggering increase in the prison population since the 1970s, despite a slight decline in recent years.
-Notably, Black men with limited education face disproportionate rates of incarceration, reflecting systemic inequalities in the justice system.
-The study examines various aspects of incarceration, including its effects on crime rates, labor markets, and family dynamics, revealing persistent challenges in prisoner rehabilitation and societal reintegration.
-Furthermore, this paper offers a unique perspective on US penal institutions as 'total institutions,' where inmates experience stringent control and minimal autonomy, leading to isolation and restricted freedom.
-Key issues such as mass incarceration, the COVID-19 pandemic, violence, health challenges, and the harsh realities of solitary confinement are explored, with a focus on the high prevalence of COVID-19 cases among prisoners.
-Global comparisons of mass incarceration trends across 20 countries provide insights into the broader context of prison systems worldwide.
-By comprehensively understanding the dynamics within prisons, this paper aims to contribute to the discourse on mass incarceration and advocate for positive reforms.
-Additionally, the paper replicates and builds upon Bruce Western's findings.Data cleaning and analysis were conducted using the open-source statistical programming language `R`[@citeR], leveraging functionalities from the `tidyverse`[@tidyverse]，`ggplot2`[@ggplot2],`dplyr`[@dplyr],`readr`[@readr],`tibble`[@tibble],`stringr`[@stringr],`haven`[@haven],`openxlsx`[@openxlsx],`janitor`[@janitor],`knitr`[@knitr].
-The detailed procedures for data extraction and cleaning are expounded upon in the subsequent subsections(@sec-data).
+Over the past three decades, incarceration has become a potent force in perpetuating and exacerbating social inequality, as evidenced by extensive sociological research highlighting America's experiment with mass incarceration and its impacts on social stratification (@Wakefield).
+This trend underscores the broader societal shift towards the expansion of the penal system, marking it as one of the most salient developments in contemporary American society.
+
+Rooted in the insights from the paper "Inside the Box: Safety, Health, and Isolation in Prison" (@western2021inside), our analysis aims to illuminate the profound impacts of incarceration on the safety and health of incarcerated individuals, often overshadowed in societal discourse compared to other institutions like schools or hospitals.
+
+With a primary focus on the United States, where the concept of "mass incarceration" looms large, our investigation delves into the remarkable surge in the prison population since the 1970s, despite recent minor declines.
+Particularly noteworthy is the disproportionate rates of incarceration faced by Black men with limited education, underscoring systemic injustices within the justice system.
+Furthermore, our study comprehensively examines various dimensions of incarceration, including its implications for crime rates, labor markets, and family dynamics.
+Through this analysis, we uncover persistent challenges in prisoner rehabilitation and societal reintegration, shedding light on critical issues often overlooked in public discourse.The significance of this research lies in its contribution to understanding the multifaceted impacts of mass incarceration, both on individuals and society at large.
+By addressing the gap in knowledge regarding the health and safety implications of incarceration, we aim to inform policy discussions and advocate for reforms that prioritize the well-being of incarcerated individuals.
+
+This article is structured as follows: In @sec-data, we provide insights into the origin of the dataset utilized in the original paper, outlining the methods employed for data collection and emphasizing key features.
+Moving on to @sec-result, we replicate the original study and present three empirical markers of "mass incarceration." In @sec-dis, we delve into the health effects of mass incarceration on both offenders and prison staff during the epidemic.
+Additionally, we critically evaluate the study's limitations and propose directions for future analyses to complement this discussion.
 
@@
 All data are not obtained directly through surveys or sampling statistics; rather, they are derived through meticulous processing and calculation based on pre-existing datasets.
+
+By comprehensively understanding the dynamics within prisons, this paper aims to contribute to the discourse on mass incarceration and advocate for positive reforms.
+Additionally, the paper replicates and builds upon Bruce Western's findings.Data cleaning and analysis were conducted using the open-source statistical programming language `R`[@citeR],leveraging functionalities from the `tidyverse`[@tidyverse],`ggplot2`[@ggplot2],`dplyr`[@dplyr],`readr`[@readr],`tibble`[@tibble],`stringr`[@stringr],`haven`[@haven],`openxlsx`[@openxlsx],`janitor`[@janitor],`knitr`[@knitr].
 
@@
 Utilizing diverse sources such as surveys, administrative records, and inmate censuses, BJS produces precise estimates of the total number of individuals held in correctional facilities.
+
 For @fig-admit and @fig-plane,original data comes from two prison questionnaires    
@@
 
-# Result
+# Result {#sec-result}
 ## Over trend
@@
 
-# Discussion
+# Discussion {#sec-dis}
 ## rehabilitating

### 2024-02-15 outputs/paper/paper.qmd
update

@@
 
-\ Data regarding prison population rates per 100,000 of the national population is accessible through the online public data platform World Prison Brief.
+Data regarding prison population rates per 100,000 of the national population is accessible through the online public data platform World Prison Brief.
 This resource provides updated country information on a monthly basis, drawing primarily from governmental or other authoritative sources, thereby ensuring the data's timeliness and reliability.
 
-\ After acquiring the most recent data, we encountered complexity in processing the information for over 200 countries.
+After acquiring the most recent data, we encountered complexity in processing the information for over 200 countries.
 Consequently, we streamlined our analysis by selecting a subset of 20 representative countries.
@@
 
-\ In addition to the United States, which serves as the primary focus of our research, the selected subset of 19 countries encompasses a diverse range of geographical locations across all seven continents.
+In addition to the United States, which serves as the primary focus of our research, the selected subset of 19 countries encompasses a diverse range of geographical locations across all seven continents.
 These countries represent various levels of development, including developed nations, developing regions, and areas classified as less economically developed.
@@
 
-\ It can be readily inferred from graphical representations and pertinent research that the United States holds the title of the world's foremost incarcerator, detaining a higher percentage of its population than any other nation.
+It can be readily inferred from graphical representations and pertinent research that the United States holds the title of the world's foremost incarcerator, detaining a higher percentage of its population than any other nation.
 
-\ It is noteworthy that the incarceration rates (per 100,000) observed in the other 19 countries typically hover around 100.
+It is noteworthy that the incarceration rates (per 100,000) observed in the other 19 countries typically hover around 100.
 In stark contrast, the United States exhibits an incarceration rate exceeding four times this average.
@@
 # Discussion {#sec-dis}
+## What is done in this paper
+Through rigorous data collection, cleaning, and analysis procedures, we meticulously obtained vital incarceration rate data spanning from 1925 to 2018 for the United States.
+Additionally, we meticulously compiled statistics on Men’s cumulative imprisonment risk, organized by cohort, and meticulously gathered data on the incarceration rates of 20 countries worldwide, including the United States, up to 2023.
+
+Delving into the phenomenon of mass incarceration, we meticulously examined its historical underpinnings, contemporary trajectories, and global ramifications.
+Our analysis underscores the staggering surge in the U.S.
+prison population since the 1970s, notwithstanding recent marginal declines, underscoring the persistent urgency in addressing the pervasive social issue of mass incarceration.
+Moreover, our study illuminates pronounced racial disparities in incarceration rates, particularly shedding light on the disproportionate impact on individuals from the Black community with limited educational opportunities.
+
+Furthermore, we provide a comprehensive exploration of global perspectives on mass incarceration, revealing the United States as the foremost incarcerator globally compared to other nations.
+Subsequently, we delve into the critical implications of mass incarceration, particularly examining its profound effects on American society.
+This includes an in-depth examination of the United States’ rehabilitation policies for incarcerated individuals, alongside an analysis of the prevalence of COVID-19 infections in American prisons during the epidemic.
+Additionally, we scrutinize the impact of relevant policies on the personnel involved in the prison system, offering valuable insights into the broader societal repercussions of mass incarceration.
+
 ## rehabilitating
@@
 
-\ The significant number of individuals held in incarceration across the United States, combined with prevalent environmental conditions within correctional facilities—such as overcrowding, limited sanitation, inadequate healthcare access, subpar ventilation, and challenges in maintaining social distancing—have presented distinct and substantial challenges and risks for both incarcerated individuals and staff members throughout the pandemic (@nowotny2020covid).
+The significant number of individuals held in incarceration across the United States, combined with prevalent environmental conditions within correctional facilities—such as overcrowding, limited sanitation, inadequate healthcare access, subpar ventilation, and challenges in maintaining social distancing—have presented distinct and substantial challenges and risks for both incarcerated individuals and staff members throughout the pandemic (@nowotny2020covid).
 
-\ @novisky2020institutional indicates that the implementation of varied epidemic prevention policies across different states in the United States, alongside differences in the infrastructure of state prisons, has resulted in significant disparities in prisoner infection rates.
+@novisky2020institutional indicates that the implementation of varied epidemic prevention policies across different states in the United States, alongside differences in the infrastructure of state prisons, has resulted in significant disparities in prisoner infection rates.
 
-\ In addition to replicating the original data, we have incorporated a comparison of the COVID-19 infection rate among prison staff with the overall U.S.
+In addition to replicating the original data, we have incorporated a comparison of the COVID-19 infection rate among prison staff with the overall U.S.
 COVID-19 infection rate.
@@
 
-\ On the other hand, when examining racial data, it tends to be categorized broadly into whites and blacks.
+On the other hand, when examining racial data, it tends to be categorized broadly into whites and blacks.
 This practice not only reinforces the binary opposition between these two racial groups in the United States but also overlooks the experiences of other ethnic minorities.

### 2024-02-15 outputs/paper/paper.qmd
update

@@
 ## Source
-The paper used for replication is Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside), which mainly analyzes the impact of prisons on safety and health, and
-specifically includes data from the new coronavirus pandemic.
 
-Sourcebook of Criminal Justice Statistics   
-Bureau of Justice Statistics Report      
-Jail Inmates in 2018, U.S. Population FRED Data     
-World Prison Population Data      
-Western B. and Pettit B data      
-Survey of Inmates of States Correctional Facilities (1986, 1991, 1997, 2004)    
+The paper used for replication is Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside), which mainly analyzes the impact of prisons on safety and health, and specifically includes data from the new coronavirus pandemic.
+
+Sourcebook of Criminal Justice Statistics\
+Bureau of Justice Statistics Report\
+Jail Inmates in 2018, U.S. Population FRED Data\
+World Prison Population Data\
+Western B. and Pettit B data\
+Survey of Inmates of States Correctional Facilities (1986, 1991, 1997, 2004)\
 Survey of Prison Inmates (2016) (Bureau of Justice Statistics 1994, 2004a, 2004b, 2006, 2019, 2021)
@@
 ## Methodology
+
 All data are not obtained directly through surveys or sampling statistics; rather, they are derived through meticulous processing and calculation based on pre-existing datasets.
@@
 ## data cleaning and construction
-Accurate data cleansing and structuring are paramount in research.
-Given the extensive and varied raw data analyzed in the original paper Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside) and the lack of detailed explanation regarding data processing methods by the original author, Figures 1, 2, 4, 5, 6, and 7 are derived from processed data provided by the original author, albeit with a distinct focus in visualization.
-For figure 2, we obtained the updated version of the original data and expanded it by incorporating data from an additional 5 countries to enhance comprehensiveness.
-@tbl-country
+
+In research, accurate data cleansing and structuring are imperative.
+Figures 1, 3, 4, 5, 6, and 7 in this study stem from the original paper Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside).
+However, due to the original author's lack of detailed explanation regarding data processing methods, we took steps to ensure the reliability and relevance of the data.
+Specifically, we focused on visualizing the processed data to enhance clarity and understanding.
+
+For Figure 2, we not only obtained the updated version of the original data but also expanded it by including data from an additional 5 countries, as outlined in @tbl-country.
+This expansion was undertaken to augment the comprehensiveness of our analysis.
+However, to maintain the relevance and accuracy of the displayed data, we made a deliberate decision not to include countries with missing data sources from the website.
 
@@
 ## Measurement
-For @fig-over
-The Bureau of Justice Statistics (BJS) conducts thorough data collection and analysis on the populations incarcerated in both state and federal prisons, as well as local jails, across the United States.
+
+For @fig-over The Bureau of Justice Statistics (BJS) conducts thorough data collection and analysis on the populations incarcerated in both state and federal prisons, as well as local jails, across the United States.
 Utilizing diverse sources such as surveys, administrative records, and inmate censuses, BJS produces precise estimates of the total number of individuals held in correctional facilities.
 
-For @fig-admit and @fig-plane,original data comes from two prison questionnaires    
+For @fig-admit and @fig-plane,original data comes from two prison questionnaires\
 For example, the sample for the 2004 survey was drawn from two different documents.
@@
 # Result {#sec-result}
+
 ## Over trend
@@
 @fig-over
+
 ```{r fig.height=10, fig.width=6 }
@@
 ## Exploring Racial Disparities in Incarceration Trends
+
 Despite extensive discussions surrounding the surge in the U.S.
@@
 ## Global Perspectives on Mass Incarceration
+
 In addition to examining the trajectory of incarceration rates within the United States over time, it is equally imperative to conduct horizontal comparisons by scrutinizing incarceration rates across different countries.
@@
 
-c_data <- data[order(-data$prison_population_rate), ]
+c_data <- data[order(-data$prison_rate_per100000), ]
 
 # Create the bar plot
-plot <- ggplot(c_data, aes(x =prison_population_rate, y = country)) +
+plot <- ggplot(c_data, aes(x =prison_rate_per100000, y = country)) +
   geom_bar(stat = "identity", fill = "skyblue") +
   theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5)) +  # Rotate x-axis labels
-  labs(x = "Prison Population Rate", y = "country")  # Add axis labels
+  labs(x = "Prison Rate (per 100,000)", y = "country")  # Add axis labels
 
@@
 # Discussion {#sec-dis}
+
 ## What is done in this paper
+
 Through rigorous data collection, cleaning, and analysis procedures, we meticulously obtained vital incarceration rate data spanning from 1925 to 2018 for the United States.
@@
 ## rehabilitating
+
 Rehabilitation refers to a series of interventions aimed at enhancing functioning and diminishing disability in individuals with health conditions, taking into account their interactions with the environment.Academics studying mass incarceration identify the 1970s as a critical juncture in U.S.
@@
 ```
+
 The original data table exclusively focused on a subset of admitted individuals for the analysis of the American Prison Rehabilitation Program.
@@
 ## Cumulative COVID-19 Case Rates among Those in Prison and General Population
+
 The closed and densely populated environment within prisons creates ideal conditions for the proliferation of large infectious diseases.
@@
 This observation underscores the vulnerable position of prisoners within correctional facilities during the pandemic.
+
 ```{r fig.height=10, fig.width=10 }
@@
 ## Weaknesses
+
 ### Bias in Data Analysis
+
 On one hand, it's noteworthy that a considerable portion of data regarding U.S.
@@
 ### Measurement error
+
 Utilizing data from various origins, a practice known as data fusion or integration, introduces complexities and hurdles that can result in measurement inaccuracies.
@@
 ## future
+
 On the one hand, similar data collection, statistical analysis, and comparative studies of Canadian prisons provide an attractive avenue for gaining insights due to Canada's geographic proximity to the United States and some shared cultural and legal frameworks.

### 2024-02-15 scripts/02-data_cleaning.R

@@ -23,7 +23,7 @@ cleaned_data <-
                        "France","Austria", "Italy","Belgium","Switzerland",
                        "Ireland", "Germany" ,"Denmark" ,"Norway","Netherlands", "Sweden",
                        "Finland","Egypt","Canada","Norway","Singapore","Japan","Iceland")) |>  # Filter specific countries
-  rename(country = title)  # Rename 'title' column to 'country'
-
+  rename(country = title)|>  # Rename 'title' column to 'country'
+  rename(prison_rate_per100000 = prison_population_rate)
 # Save the cleaned data to a new CSV file
 write_csv(cleaned_data, "outputs/data/clean_country_data.csv")

### 2024-02-15 outputs/paper/paper.qmd
update according to the reviews

@@
 
-Rooted in the insights from the paper "Inside the Box: Safety, Health, and Isolation in Prison" (@western2021inside), our analysis aims to illuminate the profound impacts of incarceration on the safety and health of incarcerated individuals, often overshadowed in societal discourse compared to other institutions like schools or hospitals.
+Rooted in the insights from the paper [*Inside the Box: Safety, Health, and Isolation in Prison*](#) (@western2021inside), our analysis aims to illuminate the profound impacts of incarceration on the safety and health of incarcerated individuals.
 
@@
 By addressing the gap in knowledge regarding the health and safety implications of incarceration, we aim to inform policy discussions and advocate for reforms that prioritize the well-being of incarcerated individuals.
+
+Our estimand aims to assess the extent of mass incarceration within the country using the incarceration rate (per 100,000 population).
+Additionally, we seek to compare the incidence rate of new coronavirus infections among incarcerated individuals with that of the general population in the United States during the epidemic.
+This comparison will provide insights into the health status and vulnerability of the prison population relative to the broader community.
 
@@
 
-The paper used for replication is Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside), which mainly analyzes the impact of prisons on safety and health, and specifically includes data from the new coronavirus pandemic.
+The paper selected for replication, [*Inside the Box: Safety, Health, and Isolation in Prison*](#) (@western2021inside), primarily investigates the impacts of prisons on safety and health, with a specific focus on data pertaining to the new coronavirus pandemic.
 
-Sourcebook of Criminal Justice Statistics\
-Bureau of Justice Statistics Report\
-Jail Inmates in 2018, U.S. Population FRED Data\
-World Prison Population Data\
-Western B. and Pettit B data\
-Survey of Inmates of States Correctional Facilities (1986, 1991, 1997, 2004)\
-Survey of Prison Inmates (2016) (Bureau of Justice Statistics 1994, 2004a, 2004b, 2006, 2019, 2021)
+This paper draws from a variety of sources, including:
+
+- @bjs1994
+- @BJS2004a,@BJS2004b,@BJS2006
+- @BJS2019,@BJS2020,@BJS2021
+- @Western2010
+- @Sourcebook2011,@Sourcebook2012,
+- @ICJPR2023
+- @BEA
+- @PADOC2018
+- @Carson2020,@Carson2020b
+- @Zeng2020
+- @NCHS2021
+- @CensusBureau
+- @COVIDPrisonProject2020,@COVIDTrackingProject2021
+
+These diverse sources provide a comprehensive foundation for the replication analysis, enabling a thorough examination of the various dimensions of incarceration and its effects on safety, health, and societal dynamics.
 
@@
 By comprehensively understanding the dynamics within prisons, this paper aims to contribute to the discourse on mass incarceration and advocate for positive reforms.
-Additionally, the paper replicates and builds upon Bruce Western's findings.Data cleaning and analysis were conducted using the open-source statistical programming language `R`[@citeR],leveraging functionalities from the `tidyverse`[@tidyverse],`ggplot2`[@ggplot2],`dplyr`[@dplyr],`readr`[@readr],`tibble`[@tibble],`stringr`[@stringr],`haven`[@haven],`openxlsx`[@openxlsx],`janitor`[@janitor],`knitr`[@knitr].
+Additionally, the paper replicates and builds upon Bruce Western's findings.Data cleaning and analysis were conducted using the open-source statistical programming language `R`[@citeR], leveraging functionalities from the `tidyverse`[@tidyverse],  `ggplot2`[@ggplot2], `dplyr`[@dplyr], `readr`[@readr], `tibble`[@tibble],`stringr`[@stringr], `haven`[@haven], `openxlsx`[@openxlsx], `janitor`[@janitor], `knitr`[@knitr].
 
@@
 In research, accurate data cleansing and structuring are imperative.
-Figures 1, 3, 4, 5, 6, and 7 in this study stem from the original paper Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside).
+@fig-over, @fig-men, @fig-admit, @fig-plane, @fig-planes, and @fig-staff in this study stem from the original paper Inside the Box: Safety, Health, and Isolation in Prison (@western2021inside).
 However, due to the original author's lack of detailed explanation regarding data processing methods, we took steps to ensure the reliability and relevance of the data.
@@
 
-For Figure 2, we not only obtained the updated version of the original data but also expanded it by including data from an additional 5 countries, as outlined in @tbl-country.
+For @fig-country, we not only obtained the updated version of the original data but also expanded it by including data from an additional 5 countries, as outlined in @tbl-country.
 This expansion was undertaken to augment the comprehensiveness of our analysis.
 However, to maintain the relevance and accuracy of the displayed data, we made a deliberate decision not to include countries with missing data sources from the website.
+
+It's crucial to clarify that the "prison rate" isn't simply the quotient of incarcerated individuals divided by the total population.
+Rather, it represents the number of individuals confined to prison facilities per 100,000 people within the broader population.
+This measurement standardizes the comparison of incarceration levels across different populations, accounting for variations in population size.
+For instance, a prison rate of 500 per 100,000 signifies that 500 individuals out of every 100,000 in the general population are incarcerated, providing a standardized metric for evaluating imprisonment prevalence across diverse demographic groups and geographic regions.
 
@@
 #| warning: false
-#| tbl-cap: prison rates in 20 countries
+#| tbl-cap: prison rate per 1000000 in 20 countries in 2023
 
@@
 
-For @fig-over The Bureau of Justice Statistics (BJS) conducts thorough data collection and analysis on the populations incarcerated in both state and federal prisons, as well as local jails, across the United States.
-Utilizing diverse sources such as surveys, administrative records, and inmate censuses, BJS produces precise estimates of the total number of individuals held in correctional facilities.
+In @fig-over, data from the Bureau of Justice Statistics (BJS) provides comprehensive insights into the populations incarcerated in state and federal prisons, as well as local jails, across the United States.
+Through meticulous data collection and analysis methods, including surveys, administrative records, and inmate censuses, the BJS offers precise estimates of the total number of individuals held in correctional facilities.
 
-For @fig-admit and @fig-plane,original data comes from two prison questionnaires\
-For example, the sample for the 2004 survey was drawn from two different documents.
-The primary archive includes a list of 1,549 state prisons from the June 30, 2000, BJS 2000 Census of State and Federal Correctional Facilities.
-The secondary archive includes 36 prisons open between June 30, 2000, and April 1, 2003.
-The sampling design required a stratified two-stage selection process.
-In the initial phase, 14 male and 7 female facilities were identified based on the gender ratio within prisons.
-The remaining facilities are divided into 16 levels based on geographic region and the male and female population within each prison.
-The weighting procedure involves assigning each inmate a base weight and three adjustment factors to obtain the final weight for the survey.
-Data was collected through face-to-face interviews with prisoners using computer-assisted personal interviewing techniques.
+In @fig-men, the measurement in question assesses the percentage of men who have experienced incarceration up to two specific points in time: 1979 for individuals born between 1945 and 1949, and 2009 for those born between 1975 and 1979.
+This measurement considers race and educational attainment as variables and distinguishes between three groups: all men, men without college education, and men with less than twelve years of completed schooling.
+
+For @fig-country, The World Prison Population List(@ICJPR2023) is compiled from a variety of sources.
+In almost all cases the original source is the national prison administration of the country concerned, or else the Ministry responsible for the prison administration.
+It's crucial to clarify that the "prison rate" isn't simply the quotient of incarcerated individuals divided by the total population.
+Rather, it represents the number of individuals confined to prison facilities per 100,000 people within the broader population.
+
+For Figures @fig-admit and @fig-plane, the original data is sourced from two prison questionnaires.
+For instance, the sample for the 2004 survey was drawn from two distinct documents.
+The primary archive comprises a list of 1,549 state prisons from the June 30, 2000, BJS 2000 Census of State and Federal Correctional Facilities.
+Meanwhile, the secondary archive includes 36 prisons operational between June 30, 2000, and April 1, 2003.
+The sampling design necessitated a stratified two-stage selection process.
+Initially, 14 male and 7 female facilities were identified based on the gender ratio within prisons.
+Subsequently, the remaining facilities were divided into 16 levels according to geographic region and the male and female population within each prison.
+The weighting procedure involved assigning each inmate a base weight and three adjustment factors to derive the final weight for the survey.
+Data collection was conducted through face-to-face interviews with prisoners utilizing computer-assisted personal interviewing techniques.
+
+The original study involved the utilization of a complex dataset derived from questionnaire surveys.
+The author meticulously filtered and cleaned this dataset, followed by the calculation of weights (albeit without detailed explanation).
+These weights were instrumental in determining the participation rates of incarcerated individuals in various programs, including drug rehabilitation, education, job training, and work assignments.
+
+To measure the cumulative COVID-19 case rates among those in prison and the general population, by state, from March 2020 to January 2021, for @fig-planes, follow these steps:
+
+1. **Define the Population:** The populations of interest are individuals incarcerated in prisons and the general population of each state in the United States.
+
+2.
+**Gather Data:** Obtain data on the total number of confirmed COVID-19 cases among individuals incarcerated in prisons and the general population of each state.
+This data can be sourced from state health departments, corrections departments, or other reliable sources tracking COVID-19 statistics.
+
+3.
+**Determine the Time Period:** Specify the time frame for which you want to calculate the cumulative case rates, starting from March 2020 (when the pandemic was declared) and ending in January 2021.
+
+4. **Calculate the Cumulative Case Rates:** For each state:
+    - For incarcerated individuals: Divide the total number of confirmed COVID-19 cases among those in prison by the total incarcerated population in prisons for that state.
+Multiply the result by 100,000 to express the rate per 100,000 incarcerated individuals.
+    - For the general population: Divide the total number of confirmed COVID-19 cases in the general population by the total population of the state.
+Multiply the result by 100,000 to express the rate per 100,000 people in the general population.
+
+Subsequent chapters (@sec-weak) will delve into comprehensive discussions regarding biases and potential errors inherent in the measurement process.
 
@@
 
-Mass incarceration, as outlined by Garland (2001), refers to the historical phenomenon characterized by exceptionally high rates of imprisonment, particularly affecting marginalized populations.
-It signifies the confinement of vast numbers of individuals within prisons, coupled with the enduring legal and financial barriers they encounter upon reintegration into society, as described by Younes (2014).
+Mass incarceration, as outlined by @garland2001introduction, refers to the historical phenomenon characterized by exceptionally high rates of imprisonment, particularly affecting marginalized populations.
+It signifies the confinement of vast numbers of individuals within prisons, coupled with the enduring legal and financial barriers they encounter upon reintegration into society, as described by @phelps2016inequality.
 
-From 1925 to 1972, the incarceration rate in the United States exhibited a period of relative stability, punctuated by minor fluctuations.
+According to @fig-over, from 1925 to 1972, the incarceration rate in the United States exhibited a period of relative stability, punctuated by minor fluctuations.
 However, since the 1970s, the number of inmates in the U.S.
-has surged dramatically, increasing by over sixfold, as noted by Manza and Uggen (2006: 95).
+has surged dramatically, increasing by over sixfold, as noted by @manza2004punishment.
 Following its peak in 2007, incarceration rates have seen a slight decline over the past decade.
@@
 This underscores the continued importance of mass incarceration as a pressing issue in the United States.
-It highlights the need for further research to fully examine its effects on various aspects including health, property ownership and personal growth.
+It highlights the need for further research to fully examine its effects on various aspects including health, property ownership, and personal growth.
 Furthermore, understanding its socioeconomic impact and exploring effective rehabilitation and reintegration strategies are important steps to address this multifaceted problem and build a more just and equitable society.
-@fig-over
 
@@
 
-After acquiring the most recent data, we encountered complexity in processing the information for over 200 countries.
+Upon acquiring the most recent data, we encountered complexity in processing the information for over 200 countries.
 Consequently, we streamlined our analysis by selecting a subset of 20 representative countries.
-Subsequently, we utilized this refined dataset to generate informative charts and visualizations(@fig-country)
+Subsequently, we utilized this refined dataset to generate informative charts and visualizations (@fig-country).
 
@@
 #| label: fig-country
-#| fig-cap: Prison Population Rate by Country
+#| fig-cap: Prison Population Rate by Country in 2023
 #| echo: false
@@
 par(fig=c(.1,1,0,1))
-plot(ccr[o1,2], 1:n1, pch="", xlim=c(0,800), xlab="", ylab="", yaxt='n')
+plot(ccr[o1,2], 1:n1, pch="", xlim=c(0,800),
+     xlab="Cumulative Case Rate (per 1000)", ylab="", yaxt='n')
 abline(h=1:n1, lty=5, col="gray")
@@
 
-plot(ccr[o1, 2], 1:n1, pch="", xlim=c(0, 800), xlab="", ylab="", yaxt='n')
+plot(ccr[o1, 2], 1:n1, pch="", xlim=c(0, 800), xlab="Cumulative Case Rate (per 1000)", ylab="", yaxt='n')
 abline(h=1:n1, lty=5, col="gray")
@@
 
-## Weaknesses
+## Weaknesses {#sec-weak}
 
@@
 
+\newpage
+
 # References

### 2024-02-15 scripts/01-download_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from World Prison Brief
+# Author: Sirui Tan 
+# Date: 10 February 2024 
+# Contact: sirui.tan@utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 #### Workspace setup ####
 library(rvest)

### 2024-02-15 scripts/02-data_cleaning.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw data to gain just 20 countries data.
+# Author:  Sirui Tan
+# Date: 10 February 2024 
+# Contact: sirui.tan@utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-02-15 scripts/03-test_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Tests the real data
 # Author: Sirui Tan
-# Date: 14 February 2024 
+# Date: 10 February 2024 
 # Contact: sirui.tan@utoronto.ca 
 # License: MIT
 # Pre-requisites: No

### 2024-02-15 scripts/04-replicate.R
update

@@ -99,16 +99,19 @@ ggplot(men_data, aes(x = race, y = risk, fill = education)) +
 # Save the plot to a file
 ggsave(filename = "outputs/graphs/Men’s_cumulative_imprisonment_risk_cohort.png",  width = 10, height = 6)
 
+
 ## CREATE FIGURE 3
-c_data <- data[order(-data$prison_population_rate), ]
+c_data <- data[order(-data$prison_rate_per100000), ]
 
 # Create the bar plot
-plot <- ggplot(c_data, aes(x =prison_population_rate, y = country)) +
+plot <- ggplot(c_data, aes(x =prison_rate_per100000, y = country)) +
   geom_bar(stat = "identity", fill = "skyblue") +
   theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5)) +  # Rotate x-axis labels
-  labs(x = "Prison Population Rate", y = "country")  # Add axis labels
+  labs(x = "Prison Rate (per 100,000)", y = "country")  # Add axis labels
 # Save the plot to a file
 ggsave(filename = "outputs/graphs/Prison_population_rate_by_country.png",  width = 10, height = 6)
+
+
 
 
 ## CREATE FIGURE 4
@@ -130,6 +133,80 @@ dimnames(drugev) <- dimnames(vocev) <- dimnames(work) <- dimnames(edev) <-
   list(NULL, c("region","year","xbar"))
 
 pdf("outputs/graphs/programs_1.pdf",height=6, width=8)
+par(mfrow=c(1,4))
+par(fig=c(0,.29, 0,1))
+plot(drugev[drugev[,"region"]==1,"year"],
+     drugev[drugev[,"region"]==1,"xbar"]*100,
+     type="b", pch=16, main="Drug Program",
+     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
+     axes=F, ylab="Percent", xlab="")
+axis(1)
+axis(2)
+lines(drugev[drugev[,"region"]==2,"year"], drugev[drugev[,"region"]==2,"xbar"]*100,
+      type="b", pch=17, col="dodgerblue")
+lines(drugev[drugev[,"region"]==3,"year"], drugev[drugev[,"region"]==3,"xbar"]*100,
+      type="b", pch=18, col="red")
[…]

### 2024-02-15 scripts/03-test_data.R
update more tests

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Tests the real data
+# Purpose: Tests the real datas
 # Author: Sirui Tan
 # Date: 10 February 2024 
 # Contact: sirui.tan@utoronto.ca 
@@ -12,6 +12,9 @@
 
 library(tidyverse)
 library(readxl)
+library(testthat)
+library(testthat)
+library(here)
 
 
 #### Test real_data_1 ####
@@ -32,6 +35,7 @@ cat("Minimum year is 1925:", min_year_check, "\n")
 cat("Maximum year is 2019:", max_year_check, "\n")
 cat("Minimum prison rate is >= 0:", min_prison_rate_check, "\n")
 
+#### Test real_data_2 ####
 file_path <- here::here("inputs/data/mass incarceration.xlsx")
 # Read the Excel file
 real_men_data <- read.xlsx(file_path, sheet = 3)
@@ -45,3 +49,37 @@ risk_check <- min(real_men_data$risk) >= 0
 # Print the test results
 cat("Unique races are 'W' and 'B':", race_check, "\n")
 cat("Minimum risk is >= 0:", risk_check, "\n")
+
+
+
+#### Test real_data_3 ####
+library(testthat)
+library(readxl)
+library(here)
+
+library(testthat)
+library(here)
+
+# Load the data
+data_3 <- read_dta(file = here::here("inputs/data/spi86to16.dta"))
+
+# Test 1: Check if the data frame has the correct number of rows
+expect_equal(nrow(data_3), 62892)
+
+# Test 2: Check if the data frame has the correct number of columns
+expect_equal(ncol(data_3), 8)
+
+# Test 3: Check if all columns are of numeric data type
+expect_true(all(sapply(data_3, is.numeric)))
+
+# Test 4: Check if all values in the 'region' column are within the expected range (1-4)
+expect_true(all(data_3$region >= 1 & data_3$region <= 4))
+
+# Test 5: Check if all values in the 'admit' column are  0 or 1 or NA
+expect_true(all(data_3$admit %in% c(0, 1,NA)))
+
+# Test 6: Check if all values in the 'year' column are within the expected range (1986-2016)
+expect_true(all(data_3$year >= 1986 & data_3$year <= 2016))
+
+# Display the first few rows of the data
+head(data_3)
